---
title: "Batch Compliance Report"
author: "Michael Jensen"
date: "September 2019"
output: html_notebook
---
# Program Description

**Purpose**

In order to improve the reliability of the Transparent Utah data, identify entities with non-archived and non-compliant batches and indicate the problem(s) with each non-compliant batch.

**Input(s)**

* The DSN for the ODBC to AWS.
* The DSN for the ODBC to Salesforce.
* The most-recently archived fiscal year (used in Invalid FY Report).
* The most-recently valid fiscal year (used in Invalid FY Report).

```{r}
dsn_aws <- "transpAWS"
dsn_sf  <- "Salesforce"

most_recent_archived_fy <- 2013
latest_valid_fy         <- 2020
```

**Output(s)**

* Invalid FY Report: A .csv file containing entity and batch information for any entity with an unexpected `fiscal_year` value.

* Invalid Type Report: A .csv file containing entity and batch information for any non-State of Utah entity with a `type` value not equal to `1`, `2`, `3`, or `7`.

* Invalid Batch Report: A .csv file containing entity and batch information for any non-State of Utah entity with an invalid `posting_date` or `account_number` value, and fields indicating the specific problem(s).

**Comments**

A batch is compliant if it meets the following criteria:

* `fiscal_year` is in `YYYY` format and makes sense (e.g., 0017, 2002, and 2099 are non-sensical values, as they refer to fiscal years for which Transparent Utah did not or does not yet exist).
* `type` is `1`, `2`, `3`, or `7` for non-State of Utah entities.
* `posting_date` makes sense, given the corresponding `fiscal_year` (e.g., `1940-04-25` isn't valid).
* For non-LEA and non-Higher Ed entities, `account_number` meets the following requirements:
  * A 19-character string in "###-######-########" format.
  * Contains a valid 3-character fund code.
  * Contains a valid 6-character function code.
  * Contains a valid 8-character account code for the corresponding transaction type (i.e., a revenue transaction must not have an account code indicating an expense transaction).
* For LEAs, `account_number` meets the following requirements:
  * A 25-character string in "##-###-####-####-###-####." format.
  * For expense transactions, `account_number` ends in "0000."
  * For revenue transactinos, `account_number` does not end in "0000."

OSA Uniform Chart of Accounts:

In the future, the OSA Uniform Chart of Accounts file will be updated. The update may change the format of the report, which means the code in the "UCoA" section of this report may need to be updated as well.

# Libraries and Data Source(s)

```{r}
library(lubridate)
library(magrittr)
library(odbc)
library(readxl)
library(splitstackshape)
library(stringr)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_sf)

rm(dsn_aws, dsn_sf)

download.file(
  "http://financialreports.utah.gov/chartofaccounts/ChartofAccountFull.xlsx",
  "ucoa.xlsx",
  mode = "wb")
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}
  #   batch_id (num): The batch's Transparency ID.
  #   begin_fy (Date): The first day of the entity's fiscal year.
  #   field_name (char): The name of the field to query.
  #   govt_type (char): The type of government (e.g., City).
  #   sf_id (char): The entity's Salesforce ID.
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   trxn_type (num): Transaction type (1 = expense, 2 = revenue).
  #   ucoa (list): The list containing the Fund, Function, and Account codes 
  #     from OSA's Uniform Chart of Accounts.
  #   ucoa_type (char): The UCoA component to check ("funct" = function,
  #     "exp" = expense, "rev" = revenue).
```

## check_posting_date

```{r}
check_posting_date <- function(batch_id, begin_fy) {
  # Check a batch's posting_date values to determine whether they are
  # reasonable.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #   begin_fy (Date): The first day of the entity's fiscal year.
  #
  # Value:
  #   Character.
  #
  # Comments:
  #   We consider the posting_date value to be reasonable if it is within three
  #   months prior to the start of the fiscal_year value through six months
  #   after the end of the fiscal_year value. Three months ahead of the fiscal
  #   year accomodates accounts payable transactions that are billed late and 
  #   six months after the fiscal year matches the Transparency Board policy 
  #   that entities upload year-end corrections within six months of the end of
  #   the fiscal year.
  #
  #   Thus, a posting_date value in the range of October 1, 2017 through
  #   June 30, 2019 is valid if the fiscal_year value is 2018 and the batch is
  #   from an entity with a fiscal year that begins on January 1.

  date_and_fy <- 
    dbGetQuery(
      odbc_aws,
      paste("
            SELECT DISTINCT posting_date, fiscal_year
            FROM transaction
            WHERE batch_id = ", batch_id)) %>% 
    mutate(fiscal_year = as.numeric(.[["fiscal_year"]]),
           begin_fy    = !!begin_fy)
  
  # Ensure begin_fy matches fiscal_year:
  if (month(begin_fy) == 1) {
    
    year(date_and_fy$begin_fy) <- date_and_fy$fiscal_year
    
  } else {
    
    year(date_and_fy$begin_fy) <- date_and_fy$fiscal_year - 1
  }
  
  date_and_fy$interval <- 
    (date_and_fy$begin_fy - months(3)) %--% 
    (date_and_fy$begin_fy + months(18) - 1)
  
  if (all(date_and_fy$posting_date %within% date_and_fy$interval)) {
    
    ""
    
  } else {
    
    date_and_fy %>% 
      filter(!posting_date %within% interval) %>% 
      .[["posting_date"]] %>% 
      paste(collapse = ", ")
  }
}
```

## check_account_number

```{r}
check_account_number <- function(batch_id, govt_type, ucoa) {
  # Check whether a batch has valid Chart of Accounts codes.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #   govt_type (char): The type of government (e.g., City).
  #   ucoa (list): The list containing OSA's Uniform Chart of Accounts Fund,
  #     Function, and Account codes.
  #
  # Value:
  #   Tibble.
  #
  # Comments:
  #   Because type 3 (payroll) information is not required to have a UCoA code
  #   and we do not require entities to upload type 7 (balance sheet)
  #   information, I decided to exlude those transaction types here.
  #
  #   Higher Education entities have not been required to report a chart of 
  #   accounts number (as of 2019-09-26), so the only purpose of including them 
  #   here is to remind us that they aren't reporting that information.
  #
  #   LEAs use a chart of accounts defined by USBE.
  
  ucoa_reported <-
    dbGetQuery(
      odbc_aws,
      paste("
            SELECT DISTINCT type, account_number
            FROM transaction
            WHERE batch_id = ", batch_id, "
            AND type IN (1, 2)")) %>%
    as_tibble()

  invalid_ucoa_info <- 
    tibble(
      batch_id            = batch_id,
      any_blank_or_na     = NA,
      incorrect_format    = NA,
      invalid_fund        = NA,
      invalid_funct       = NA,
      invalid_account_exp = NA,
      invalid_account_rev = NA)
  
  if (any(is.na(ucoa_reported$account_number)) || 
      any(ucoa_reported$account_number == "")) {

    invalid_ucoa_info$any_blank_or_na <- "Yes"
    
    ucoa_reported <- 
      ucoa_reported %>% 
      filter(account_number != "", !is.na(account_number))
  }
  
  # Higher Education ###########################################################
  
  if (govt_type == "Institute_of_Higher_Education") {
    
    return(invalid_ucoa_info)
  }
  
  # LEAs #######################################################################
  if (govt_type == "School_District_or_Charter_School") {
    
    if (any(
         !str_detect(
           ucoa_reported$account_number,
           regex("^[:digit:]{2}-[:digit:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$")))) {
    
    invalid_ucoa_info$incorrect_format <- 
      ucoa_reported %>% 
      filter(
        !str_detect(
          ucoa_reported$account_number,
          regex("^[:digit:]{2}-[:digit:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$"))) %>% 
      .[["account_number"]] %>% 
      paste(collapse = ", ") %>% 
      sort()
    
    ucoa_reported <- 
      ucoa_reported %>% 
      filter(
        str_detect(
          ucoa_reported$account_number,
          regex("^[:digit:]{2}-[:digit:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$")))
    }
    
    exp <- 
      ucoa_reported %>% 
      filter(type == 1) %>% 
      .[["account_number"]]
    
    rev <- 
      ucoa_reported %>% 
      filter(type ==2) %>% 
      .[["account_number"]]
    
    # "0000" is the only valid format for the last four digits in an LEA's
    # chart of accounts.
    if (length(exp) > 0 &&
        !all(str_detect(exp, regex(".0000$")))) {
      
      invalid_ucoa_info$invalid_account_exp <- 
        exp[!(str_detect(exp, regex(".0000$")))] %>% 
        unique() %>%
        paste(collapse = ", ") %>%
        sort()
    }
    
    # "0000" is not valid for the last four digits in an LEA's chart of
    # accounts.
    if (length(rev) > 0 &&
        str_detect(rev, regex(".0000$"))) {
      
      invalid_ucoa_info$invalid_account_rev <- 
        rev[(str_detect(rev, regex(".0000$")))] %>% 
        unique() %>%
        paste(collapse = ", ") %>%
        sort()
    }
    
    return(invalid_ucoa_info)
  }

  # Non-LEAs ###################################################################
  if (any(
        !str_detect(
          ucoa_reported$account_number,
          regex("^[:digit:]{3}-[:digit:]{6}-[:digit:]{8}$")))) {
    
    invalid_ucoa_info$incorrect_format <- 
      ucoa_reported %>% 
      filter(
        !str_detect(
          ucoa_reported$account_number,
          regex("^[:digit:]{3}-[:digit:]{6}-[:digit:]{8}$"))) %>% 
      .[["account_number"]] %>% 
      paste(collapse = ", ") %>% 
      sort()
    
    ucoa_reported <- 
      ucoa_reported %>% 
      filter(
        str_detect(
          ucoa_reported$account_number,
          regex("^[:digit:]{3}-[:digit:]{6}-[:digit:]{8}$")))
  }
  
  fund <- 
    ucoa_reported %>% 
    .[["account_number"]] %>% 
    substring(1, 3)
  
  funct <-
    ucoa_reported %>% 
    .[["account_number"]] %>% 
    substring(5, 10)
  
  account <- 
    ucoa_reported %>% 
    mutate(account_number = substring(account_number, 12, 19))
  
  account_exp <- 
    account %>% 
    filter(type == 1) %>% 
    .[["account_number"]]
    
  account_rev <- 
    account %>%
    filter(type == 2) %>% 
    .[["account_number"]]
  
  if (!all(fund %in% ucoa[["fund"]][["NUMBER"]])) {
    
    invalid_ucoa_info$invalid_fund <- 
      fund[!fund %in% ucoa[["fund"]][["NUMBER"]]] %>% 
      unique() %>% 
      paste(collapse = ", ") %>% 
      sort()
  }
  
  if (!all(funct %in% ucoa[["funct"]][["NUMBER"]])) {
    
    invalid_ucoa_info$invalid_funct <- 
      funct[!funct %in% ucoa[["funct"]][["NUMBER"]]] %>% 
      unique() %>% 
      paste(collapse = ", ") %>%
      sort()
  }
  
  if (!all(account_exp %in% ucoa[["account_exp"]][["NUMBER"]])) {
    
    invalid_ucoa_info$invalid_account_exp <- 
      account_exp[!account_exp %in% ucoa[["account_exp"]][["NUMBER"]]] %>% 
      unique() %>%
      paste(collapse = ", ") %>%
      sort()
  }
  
  if (!all(account_rev %in% ucoa[["account_rev"]][["NUMBER"]])) {
    
    invalid_ucoa_info$invalid_account_rev <- 
      account_rev[!account_rev %in% ucoa[["account_rev"]][["NUMBER"]]] %>% 
      unique() %>%
      paste(collapse = ", ") %>% 
      sort()
  }
  
  invalid_ucoa_info
}
```

## generate_report

```{r}
generate_report <- function(t_id, begin_fy, govt_type, name, sf_id, ucoa) {
  # Generate the batch compliance report for an entity.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   begin_fy (Date): The first day of the entity's fiscal year.
  #   govt_type (char): The type of government (e.g., City).
  #   name: The entity's name.
  #   sf_id: The entity's Salesforce ID.
  #   ucoa (list): The list containing OSA's Uniform Chart of Accounts Fund,
  #     Function, and Account codes.
  #
  # Value:
  #   Tibble.
  
  batch_ids <- 
    query_batch_ids(t_id)

  # Create a one-row tibble for entities without processed or processing 
  # batches (otherwise, R will throw an error):
  if (length(batch_ids) == 0 || nrow(batch_ids) == 0) {
    
    report <-
      tibble(
        batch_id             = NA,
        fiscal_year          = NA,
        any_blank_or_na      = NA,
        incorrect_format     = NA,
        invalid_fund         = NA,
        invalid_funct        = NA,
        invalid_account_exp  = NA,
        invalid_account_rev  = NA,
        invalid_date         = NA,
        entity_name          = NA,
        sf_id                = NA,
        upload_date          = NA,
        begin_txn_date       = NA,
        end_txn_date         = NA,
        transaction_type     = NA,
        username             = NA,
        uploaded_file        = NA,
        file_record_count    = NA,
        file_total_amount    = NA)
    
    return(report)
  }
  
  report <-
    batch_ids$batch_id %>% 
    map(check_account_number, govt_type, ucoa) %>% 
    bind_rows()   %>% 
    mutate(invalid_date = map(batch_id, check_posting_date, begin_fy),
           entity_name  = !!name,
           sf_id        = !!sf_id) %>% 
    unnest(invalid_date)
  
  report <- 
    report %>% 
    mutate(
      transaction_type    = map(batch_id, query_type),
      upload_date         = map(batch_id, query_date_field, "upload_date"),
      begin_txn_date      = map(batch_id, query_date_field, "begin_txn_date"),
      end_txn_date        = map(batch_id, query_date_field, "end_txn_date"),
      username            = map(batch_id, query_username),
      uploaded_file       = map(batch_id, query_file_name),
      file_record_count   = map(batch_id, 
                                query_batch_field, 
                                "file_record_count"),
      file_total_amount   = map(batch_id, 
                                query_batch_field, 
                                "file_total_amount"),
      entity_name         = name,
      entity_id           = sf_id,
      fiscal_year         = map(batch_id, query_fiscal_year)) %>%
    unnest(upload_date, begin_txn_date, end_txn_date, transaction_type,
           username, uploaded_file, file_record_count, file_total_amount) %>% 
    unnest(fiscal_year)
}
```

## query_batch_ids

```{r}
query_batch_ids <- function(t_id) {
  # Query an entity's processed batch IDs.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #
  # Value:
  #   Tibble.
  #
  # Comments:
  #   The 'DONTDELETE' batch status is a variation of 'PROCESSED.' DONTDELETE 
  #   indicates the data in the batch has been split among multiple transaction
  #   tables (e.g., the batch contains data for archived and non-archived 
  #   fiscal years.
  
  if (is.na(t_id)) {
    
    return(vector(mode = "numeric", length = 0)) 
  }
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT id
          FROM batch
          WHERE entity_id = ", t_id, "
          AND status IN ('PROCESSED', 'DONTDELETE')")) %>% 
    as_tibble() %>% 
    rename("batch_id" = "id")
}
```


## query_date_field

```{r}
query_date_field <- function(batch_id, field_name) {
  # Query one of a batch's date fields (e.g., upload_date).
  #
  # Arguments:
  #   field_name (char): The name of the field to query.
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Date.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT ", field_name, " AS date_field
          FROM batch
          WHERE id = ", batch_id)) %>%
    .[["date_field"]] %>% 
    as.Date()
}
```

## query_file_name

```{r}
query_file_name <- function(batch_id) {
  # Query the file name of an uploaded batch.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Character.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT upload_file
          FROM batch
          WHERE id = ", batch_id)) %>%
    .[["upload_file"]]
}
```

## query_fiscal_year

```{r}
query_fiscal_year <- function(batch_id) {
  # Query the fiscal year of a batch.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Numeric.

  dbGetQuery(
    odbc_aws,
    paste("
          SELECT DISTINCT fiscal_year
          FROM transaction
          WHERE batch_id = ", batch_id)) %>% 
    .[["fiscal_year"]] %>% 
    as.numeric()
}
```

## query_type

```{r}
query_type <- function(batch_id) {
  # Query the transaction types contained in a batch.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Character.
  #
  # Comments:
  #   As I've decided not to check type 3 (payroll) and type 7 (balance sheet)
  #   data, the only types to check here are type 1 (expense) and type 2
  #   (revenue).
  
  reported_types <- 
    dbGetQuery(
      odbc_aws,
      paste("
            SELECT DISTINCT type
            FROM transaction
            WHERE batch_id = ", batch_id))
  
  reported_types$name <- 
    if_else(reported_types$type == 1, "EXP", "REV")
  
  reported_types$name %>% 
    paste(collapse = ", ")
}
```

## query_batch_field

```{r}
query_batch_field <- function(batch_id, field_name) {
  # Query a non-date field from the Batch Table.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #   field_name (char): The name of the field to query.
  #
  # Value:
  #   Character or numeric.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT ", field_name, " AS field_name
          FROM batch
          WHERE id = ", batch_id)) %>% 
    .[["field_name"]]
}
```

## query_username

```{r}
query_username <- function(batch_id) {
  # Query the username of the person who uploaded a batch.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Character.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT upload_username
          FROM batch
          WHERE id = ", batch_id)) %>%
    .[["upload_username"]]
}
```

# Execution

## Salesforce

```{r}
sf_data <-
  dbGetQuery(
    odbc_sf,
    paste("
          SELECT
            Account.Name                  AS name,
            Account.Id                    AS id,
            Account.Transparency_ID__c    AS t_id,
            Account.Fiscal_Year_Begins__c AS begin_fy,
            RecordType.DeveloperName      AS govt_type
          FROM Account
          JOIN RecordType
          ON Account.RecordTypeId = RecordType.Id
          WHERE Account.RecordTypeId IN (
            SELECT Id
            FROM RecordType
            WHERE DeveloperName IN (
              'AOG',
              'City',
              'Conservation_District',
              'Community_Reinvestment_Agency',
              'County',
              'District_Health',
              'Housing',
              'Independent_Quasi_State_Entity',
              'Institute_of_Higher_Education',
              'Interlocal',
              'Local_and_Special_Service_District',
              'Mental_Health',
              'Redevelopment_Agency_Project_Area',
              'School_District_or_Charter_School',
              'Town'))
          AND Account.Entity_Status__c IN (
            'Current',
            'On hold',
            'Delinquent',
            'Suspended')
          AND Account.Name NOT IN (
            'Intermountain Power Agency',
            'test city 2',
            'Utah Associated Municipal Power Systems',
            'Utah Municipal Power Agency')
          AND (
            Account.Expense_Revenue_Start_Date__c <= DATE() OR
            Account.Expense_Revenue_Start_Date__c IS NULL)")) %>%
  as_tibble() %>% 
  filter(!is.na(t_id))
```

## UCoA

```{r}
ucoa_fund <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[1]])

ucoa_function <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[2]])

ucoa_account <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[3]])

# Some of the code below will become unnecessary after I edit OSA's Uniform
# Chart of Accounts and publish it on the OSA website.

colnames(ucoa_fund)     <- ucoa_fund[2, ]
colnames(ucoa_function) <- c("NUMBER", ucoa_function[1, 2:4])
colnames(ucoa_account)  <- ucoa_account[2, ]

ucoa_fund     <- ucoa_fund %>% slice(-1, -2)
ucoa_function <- ucoa_function %>% slice(-1)
ucoa_account  <- ucoa_account %>% slice(-1, -2)

extra_fund_numbers <- 
  c(202:298, 302:398, 402:448, 452:498, 502:598, 602:698, 702:798) %>% 
  as.character() %>% 
  enframe(name = NULL) %>% 
  rename("NUMBER" = "value") %>% 
  mutate("SHORT DESCRIPTION" = NA, "FULL DESCRIPTION" = NA, "DETAIL" = NA)

ucoa_fund <- 
  ucoa_fund %>% 
  bind_rows(extra_fund_numbers)

ucoa_fund$NUMBER[[1]]     <- "010"
ucoa_fund$NUMBER[[2]]     <- "020"
ucoa_fund$NUMBER[[3]]     <- "030"
ucoa_function$NUMBER[[1]] <- "000000"

ucoa_account_exp <-
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^4"))

ucoa_account_rev <- 
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^3"))
  
# ucoa_account_w2 <- 
#   ucoa_account %>% 
#   filter(str_detect(NUMBER, "^4001"))

ucoa <-
  list(
    fund        = ucoa_fund,
    funct       = ucoa_function,
    account     = ucoa_account,
    account_exp = ucoa_account_exp,
    account_rev = ucoa_account_rev)

rm(ucoa_fund, ucoa_function, ucoa_account, extra_fund_numbers, ucoa_account_exp,
   ucoa_account_rev)
```

## Reports

### Invalid FY and Type Reports

```{r}
entity_ids <- 
  dbGetQuery(odbc_aws, "SELECT id, name FROM entity")

report_invalid_fy <- 
  dbGetQuery(
    odbc_aws,
    paste("
      SELECT DISTINCT batch_id, fiscal_year, batch.entity_id
      FROM transaction
      JOIN batch
      ON transaction.batch_id = batch.id
      WHERE (
        fiscal_year <= ", most_recent_archived_fy, " AND 
        fiscal_year > ", latest_valid_fy, ")"))

if (nrow(report_invalid_fy) > 0) {
  
  report_invalid_fy <- 
    report_invalid_fy %>% 
    left_join(entity_ids, by = c("entity_id" = "id")) %>% 
    select(entity_name = name, entity_id, batch_id, fiscal_year) %>% 
    arrange(entity_name)
  
  report_invalid_fy <- 
    report_invalid_fy$batch_id %>% 
    map(
      ~ dbGetQuery(
        odbc_aws,
        paste("
          SELECT 
            batch.id AS batch_id, upload_date, upload_username, upload_file
          FROM batch
          WHERE batch.id = ", .x))) %>% 
    bind_rows() %>% 
    left_join(report_invalid_fy, by = "batch_id") %>% 
    select(entity_name, entity_id, batch_id, fiscal_year, upload_date,
           upload_username, upload_file)
}

report_invalid_type <- 
  dbGetQuery(
    odbc_aws,
    "
    SELECT DISTINCT
      batch.entity_id,
      transaction.batch_id,
      transaction.type
    FROM transaction
    JOIN batch
    ON batch.id = transaction.batch_id
    WHERE transaction.type NOT IN (1, 2, 3, 7)
    AND batch.entity_id <> 1")

if (nrow(report_invalid_type) > 0) {
  
  report_invalid_type <- 
    report_invalid_type %>% 
    left_join(entity_ids, by = c("entity_id" = "id")) %>% 
    select(entity_name = name, entity_id, batch_id, type) %>% 
    arrange(entity_name)
  
  report_invalid_type <- 
    report_invalid_type$batch %>% 
    map(
      ~ dbGetQuery(
        odbc_aws,
        paste("
          SELECT 
            batch.id AS batch_id, upload_date, upload_username, upload_file
          FROM batch
          WHERE batch.id = ", .x))) %>% 
    bind_rows() %>% 
    left_join(report_invalid_type, by = "batch_id") %>% 
    select(entity_name, entity_id, batch_id, type, upload_date, upload_username,
           upload_file) %>% 
    arrange(type)
}

rm(entity_ids)
```

### Invalid Batch Report

Code for testing the Invalid Batch Report: 

```{r, eval=FALSE}
original <- sf_data

sf_data <-
  sf_data %>%
  filter(!is.na(t_id)) %>%
  filter(t_id == 445 | # Highland City
         t_id == 299 | # Box Elder County
         t_id == 631 | # West Valley City
         t_id == 605 | # Tooele City
         t_id == 919 | # Stansbury Service Agency
         t_id == 205 | # Cache School District
         t_id == 63  | # Kane School District
         t_id == 151 | # CS Lewis Academy
         t_id == 233 | # Freedom Academy
         t_id == 7   | # Utah State University
         t_id == 3)    # University of Utah  
```

Create the Invalid Batch Report:

```{r}
entity_batches <- 
  list(
    t_id      = as.list(sf_data$t_id),
    begin_fy  = as.list(sf_data$begin_fy),
    govt_type = as.list(sf_data$govt_type),
    name      = as.list(sf_data$name),
    sf_id     = as.list(sf_data$id)) %>% 
  pmap(generate_report, ucoa)

names(entity_batches) <- sf_data$name

invalid_batches <- 
  entity_batches %>% 
  bind_rows() %>%
  select(entity_name, entity_id, batch_id, fiscal_year, 
         any_blank_or_na, incorrect_format, invalid_fund, invalid_funct,
         invalid_account_exp, invalid_account_rev, invalid_date,
         username, uploaded_file, upload_date, transaction_type,
         begin_txn_date, end_txn_date, file_record_count, 
         file_total_amount) %>%
  filter(!is.na(any_blank_or_na)     |
         !is.na(incorrect_format)    |
         !is.na(invalid_fund)        |
         !is.na(invalid_funct)       |
         !is.na(invalid_account_exp) |
         !is.na(invalid_account_rev) |
         invalid_date != "") %>% 
  arrange(entity_name, fiscal_year)

rm(entity_batches)

report_invalid_batch <- 
  sf_data %>% 
  select(entity_name = name, t_id, govt_type) %>% 
  mutate(
    any_blank_or_na            = NA,
    number_incorrect_format    = NA,
    number_invalid_fund        = NA,
    number_invalid_function    = NA,
    number_invalid_exp = NA,
    number_invalid_rev = NA,
    number_invalid_date        = NA)

for (i in 1:nrow(report_invalid_batch)) {
  
  a <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(any_blank_or_na)
  
  if (any(!is.na(a))) {
    
    report_invalid_batch$any_blank_or_na[[i]] <- "Yes"
    
  } 
  rm(a)
}
rm(i)

for (i in 1:nrow(report_invalid_batch)) {
  
  if (report_invalid_batch$govt_type[[i]] == "Institute_of_Higher_Education") {
    
    report_invalid_batch$number_incorrect_format[[i]] <- NA
    
  } else {
  
  report_invalid_batch$number_incorrect_format[[i]] <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(incorrect_format) %>% 
    filter(!is.na(incorrect_format)) %>% 
    cSplit(
      splitCols = "incorrect_format", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique() %>% 
    nrow()
  }
}
rm(i)

for (i in 1:nrow(report_invalid_batch)) {
  
  if (report_invalid_batch$govt_type[[i]] %in%
      c("School_District_or_Charter_School", 
        "Institute_of_Higher_Education")) {
    
    report_invalid_batch$number_invalid_fund[[i]] <- NA
    
  } else {
  
  report_invalid_batch$number_invalid_fund[[i]] <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(invalid_fund) %>% 
    filter(!is.na(invalid_fund)) %>% 
    cSplit(
      splitCols = "invalid_fund", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique() %>% 
    nrow()
  }
}
rm(i)

for (i in 1:nrow(report_invalid_batch)) {
  
  if (report_invalid_batch$govt_type[[i]] %in%
      c("School_District_or_Charter_School", 
        "Institute_of_Higher_Education")) {
    
    report_invalid_batch$number_invalid_function[[i]] <- NA
    
  } else {
  
  report_invalid_batch$number_invalid_function[[i]] <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(invalid_funct) %>% 
    filter(!is.na(invalid_funct)) %>% 
    cSplit(
      splitCols = "invalid_funct", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique() %>% 
    nrow()
  }
}
rm(i)

for (i in 1:nrow(report_invalid_batch)) {
  
  if (report_invalid_batch$govt_type[[i]] %in%
      c("School_District_or_Charter_School", 
        "Institute_of_Higher_Education")) {
    
    report_invalid_batch$number_invalid_exp[[i]] <- NA
    
  } else {
  
  report_invalid_batch$number_invalid_exp[[i]] <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(invalid_account_exp) %>% 
    filter(!is.na(invalid_account_exp)) %>% 
    cSplit(
      splitCols = "invalid_account_exp", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique() %>% 
    nrow()
  }
}
rm(i)

for (i in 1:nrow(report_invalid_batch)) {
  
  if (report_invalid_batch$govt_type[[i]] %in%
      c("School_District_or_Charter_School", 
        "Institute_of_Higher_Education")) {
    
    report_invalid_batch$number_invalid_rev[[i]] <- NA
    
  } else {
    
    report_invalid_batch$number_invalid_rev[[i]] <- 
      invalid_batches %>% 
      filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
      select(invalid_account_rev) %>% 
      filter(!is.na(invalid_account_rev)) %>% 
      cSplit(
        splitCols = "invalid_account_rev", 
        sep = ",", 
        direction = "long",
        type.convert = FALSE) %>%  
      unique() %>% 
      nrow()
  }
}
rm(i)

for (i in 1:nrow(report_invalid_batch)) {
  
  a <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(invalid_date) %>% 
    filter(invalid_date != "")
  
  if (length(a) > 0) {
    
    report_invalid_batch$number_invalid_date[[i]] <- 
      a %>% 
      cSplit(
        splitCols = "invalid_date", 
        sep = ",", 
        direction = "long",
        type.convert = FALSE) %>%  
      nrow()
  }
  rm(a)
}
rm(i)

report_invalid_batch <- 
  report_invalid_batch %>% 
  filter(!is.na(any_blank_or_na)                                          |
         (!is.na(number_incorrect_format) & number_incorrect_format != 0) |
         (!is.na(number_invalid_fund)     & number_invalid_fund != 0)     |
         (!is.na(number_invalid_function) & number_invalid_function != 0) |
         (!is.na(number_invalid_exp)      & number_invalid_exp != 0)      |
         (!is.na(number_invalid_rev)      & number_invalid_rev != 0))
```

```{r}
file_path <-
  "S:/Localgov/LG Compliance/Transparency Compliance/Compliance Reports/"

report_invalid_batch %>%
  write_csv(
    path = paste0(file_path, Sys.Date(), " Invalid Batch Report.csv"),
    na = "")

report_invalid_fy %>%
  write_csv(
    path = paste0(file_path, Sys.Date(), " Invalid FY Report.csv"),
    na = "")

report_invalid_type %>%
  write_csv(
    path = paste0(file_path, Sys.Date(), " Invalid Type Report.csv"),
    na = "")
```
  
## Individual Files for Invalid Data

*Note: As of 2019-07-30, Excel will round the numbers in the .csv files. Use Notepad or some other application instead when viewing the data.*

Not 19-characters:

```{r}
list_incorrect_format <- list()

for (i in 1:nrow(report_invalid_batch)) {

  list_incorrect_format[[i]] <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(incorrect_format) %>% 
    filter(!is.na(incorrect_format)) %>% 
    cSplit(
      splitCols = "incorrect_format", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_incorrect_format) <- report_invalid_batch$entity_name

for (i in names(list_incorrect_format)) {
  
  if (nrow(list_incorrect_format[[i]]) > 0) {
    
   write_csv(list_incorrect_format[[i]], paste0(i, "_incorrect_formats.csv")) 
  }
}
rm(i)
```

Number Invalid Fund:

```{r}
list_invalid_fund <- list()

for (i in 1:nrow(report_invalid_batch)) {

  list_invalid_fund[[i]] <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(invalid_fund) %>% 
    filter(!is.na(invalid_fund)) %>% 
    cSplit(
      splitCols = "invalid_fund", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_invalid_fund) <- report_invalid_batch$entity_name

for (i in names(list_invalid_fund)) {
  
  if (nrow(list_invalid_fund[[i]]) > 0) {
    
   write_csv(list_invalid_fund[[i]], paste0(i, "_invalid_fund.csv")) 
  }
}
rm(i)
```

Number Invalid Function:

```{r}
list_invalid_funct <- list()

for (i in 1:nrow(report_invalid_batch)) {

  list_invalid_funct[[i]] <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(invalid_funct) %>% 
    filter(!is.na(invalid_funct)) %>% 
    cSplit(
      splitCols = "invalid_funct", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_invalid_funct) <- report_invalid_batch$entity_name

for (i in names(list_invalid_funct)) {
  
  if (nrow(list_invalid_funct[[i]]) > 0) {
    
   write_csv(list_invalid_funct[[i]], paste0(i, "_invalid_function.csv")) 
  }
}
rm(i)
```

Number Invalid Account Exp:

```{r}
list_invalid_account_exp <- list()

for (i in 1:nrow(report_invalid_batch)) {

  list_invalid_account_exp[[i]] <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(invalid_account_exp) %>% 
    filter(!is.na(invalid_account_exp)) %>% 
    cSplit(
      splitCols = "invalid_account_exp", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_invalid_account_exp) <- report_invalid_batch$entity_name

for (i in names(list_invalid_account_exp)) {
  
  if (nrow(list_invalid_account_exp[[i]]) > 0) {
    
   write_csv(list_invalid_account_exp[[i]], paste0(i, "_invalid_account_exp.csv")) 
  }
}
rm(i)
```

Number Invalid Account Rev:

```{r}
list_invalid_account_rev <- list()

for (i in 1:nrow(report_invalid_batch)) {

  list_invalid_account_rev[[i]] <- 
    invalid_batches %>% 
    filter(entity_name == report_invalid_batch$entity_name[[i]]) %>% 
    select(invalid_account_rev) %>% 
    filter(!is.na(invalid_account_rev)) %>% 
    cSplit(
      splitCols = "invalid_account_rev", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_invalid_account_rev) <- report_invalid_batch$entity_name

for (i in names(list_invalid_account_rev)) {
  
  if (nrow(list_invalid_account_rev[[i]]) > 0) {
    
   write_csv(list_invalid_account_rev[[i]], paste0(i, "_invalid_account_rev.csv")) 
  }
}
rm(i)
```

# DBMS Disconnection

```{r}
dbDisconnect(odbc_aws, odbc_sf)
```