---
title: "mail-merge-10day-budget-notice"
author: "Alexander Nielson"
date: "2/5/2020"
output: html_document
---
# Program Description

**Purpose**

Compile and format the information needed to send the 10-day Warning postcards to local governments that are non-compliant with OSA or State Treasurer budget requirements.

*This a modified R script based on Michael Jensens "MailMerge.RMD" which can be found at his github or in the Archive folder. * 

**Input(s)**

```{r}
dsn_sf <- "Salesforce"

# Select the appropriate notice type:
notice_type <- "ten_day_budget_notice"
budget_schedule <- 
#  "fiscal_year"
"traditional_year"
```

**Output(s)**

A .csv file containing a record for each entity that is missing a required Transparent Utah report, with the following fields:

* Entity name
* Entity CFO name
* Entity CAO name
* Entity address information
* A field for each report the entity is missing

A .csv file containing a record for each entity that is missing a required budget report, with the following fields:

* Entity name
* Entity CFO name
* Entity CAO name
* Entity address information
* Tax status
* Finet code
* A field for each budget report the entity is missing

**Comments**



# Libraries and Data Sources

```{r}
library(data.table)
library(janitor)
library(magrittr)
library(odbc)
library(readxl)
library(splitstackshape)
library(svDialogs)
library(tidyverse)

odbc_salesforce <- dbConnect(odbc::odbc(), dsn_sf)

rm(dsn_sf)
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}
  # Arguments:
  #  address_one (char): The portion of the complete address corresponding to 
  #    street_one.
  #  address_two (char): The portion of the complete address corresponding to 
  #    street_two.
  #  street_one (char): The default street address.
  #  street_two (char): The street address to compare against.
```

## find_an_address()

```{r}
find_an_address <- function(street_one, street_two, address_one, address_two) {
  # Compare two street addresses and select the corresponding address 
  # information for the street address that is not NA.
  #
  # Arguments:
  #  street_one (char): The default street address.
  #  street_two (char): The street address to compare against.
  #  address_one (char): The portion of the complete address corresponding to 
  #    street_one.
  #  address_two (char): The portion of the complete address corresponding to 
  #    street_two.
  #
  # Returns:
  #   Character.
  
  if (is.na(street_one) && !is.na(street_two)) {
    
    address_two
  
  } else {address_one}
}
```

##check_fiscal_year()
```{r}

```


# Execution

## Salesforce - Contact Information

```{r}
account <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT 
      a.Id                         AS sf_id,
      a.Name                       AS entity_name, 
      r.Name                       AS record_type,
      a.Is_Solely_Fee_Assessing__c AS non_taxing_entity,
      a.ShippingStreet, a.ShippingCity, a.ShippingState, a.ShippingPostalCode,
      a.BillingStreet, a.BillingCity, a.BillingState, a.BillingPostalCode,
      a.Mailing_county__c          AS mailing_county,
      a2.Name                      AS tax_holding_county,
      a.FINET_Vendor_Code__c       AS finet_code
    FROM Account AS a
    LEFT JOIN RecordType AS r
    ON a.RecordTypeId = r.Id
    LEFT JOIN Account AS a2
    ON a.Tax_Holding_County__c = a2.Id
    WHERE a.IsDeleted = FALSE
    AND a.Entity_Status__c NOT IN ('Inactive', 'Dissolved')
    AND a.Name <> 'test city 2'
    AND a.RecordTypeId IN (
      SELECT id
      FROM RecordType
      WHERE Name IN (
        'AOG', 'City', 'Community Reinvestment Agency', 'Conservation District',
        'County', 'District Health', 'Housing', 
        'Independent/Quasi State Entity', 'Interlocal', 
        'Local and Special Service District', 'Mental Health', 'Non Profits',
        'Redevelopment Agency/Project Area', 
        'School District or Charter School', 'Town'))") %>% 
  mutate(street = pmap_chr(
                    list(
                      street_one  = as.list(ShippingStreet),
                      street_two  = as.list(BillingStreet),
                      address_one = as.list(ShippingStreet),
                      address_two = as.list(BillingStreet)),
                    find_an_address),
         city   = pmap_chr(
                    list(
                      street_one  = as.list(ShippingStreet),
                      street_two  = as.list(BillingStreet),
                      address_one = as.list(ShippingCity),
                      address_two = as.list(BillingCity)),
                    find_an_address),    
         state   = pmap_chr(
                    list(
                      street_one  = as.list(ShippingStreet),
                      street_two  = as.list(BillingStreet),
                      address_one = as.list(ShippingState),
                      address_two = as.list(BillingState)),
                    find_an_address),         
         zip     = pmap_chr(
                    list(
                      street_one  = as.list(ShippingStreet),
                      street_two  = as.list(BillingStreet),
                      address_one = as.list(ShippingPostalCode),
                      address_two = as.list(BillingPostalCode)),
                    find_an_address)) %>% 
  select(sf_id, entity_name, record_type, non_taxing_entity, 
         street, city, state, zip, mailing_county, tax_holding_county,
         finet_code)

# CFOs and CAOs sometimes have an address that is different from the entity's
# address. Though it would be more convenient for the CFO and CAO to receive the 
# notice at the address specific to their contact information, I decided to 
# send notices to the entity address. Given that the CFO and CAO can change 
# without notifying OSA, it seems that sending the notice to the entity's 
# address is the best way to make sure that someone within the entity 
# organization will see it.

cfo <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT
      a.Name            AS entity_name, 
      c.Name            AS cfo_name
      -- MailingStreet     AS cfo_street, 
      -- MailingCity       AS cfo_city, 
      -- MailingState      AS cfo_state, 
      -- MailingPostalCode AS cfo_zipcode
    FROM Contact AS c
    JOIN Account AS a
    ON c.AccountId = a.Id
    WHERE c.IsDeleted = FALSE
    AND c.IsDeactivated__c = FALSE
    AND Role__c = 'CFO'")

cao <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT
      a.Name            AS entity_name, 
      c.Name            AS cao_name
      -- MailingStreet     AS cao_street, 
      -- MailingCity       AS cao_city, 
      -- MailingState      AS cao_state, 
      -- MailingPostalCode AS cao_zipcode
    FROM Contact AS c
    JOIN Account AS a
    ON c.AccountId = a.Id
    WHERE c.IsDeleted = FALSE
    AND c.IsDeactivated__c = FALSE
    AND Role__c = 'CAO'")

# Check for entities with multiple CFOs:
multiple_cfos <- 
  cfo[duplicated(cfo$entity_name), "entity_name"] %>% 
  tibble(has_multiple_cfos = .) %>% 
  distinct(has_multiple_cfos) %>% 
  arrange(has_multiple_cfos)

multiple_caos <- 
  cao[duplicated(cao$entity_name), "entity_name"] %>% 
  tibble(has_multiple_caos = .) %>% 
  distinct(has_multiple_caos) %>% 
  arrange(has_multiple_caos)

if (nrow(multiple_cfos) > 0 || nrow(multiple_caos) > 0) {
  
  dlg_message(
    "Salesforce has at least one entity with multiple CFOs or CAOs.
    See report of entities with multiple cfos or caos.
    This program will select one of the names to send a notice to.")
  
  file_path <-
    "S:/Localgov/Database/Salesforce/Reports/"
  
  multiple_cfos %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), " Entities with Multiple CFOs.csv"),
      na = "")
  
  multiple_caos %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), " Entities with Multiple CAOs.csv"),
      na = "")
  
  cfo <- 
    cfo %>% 
    data.table() %>% 
    unique(by = "entity_name")

  cao <- 
    cao %>% 
    data.table() %>% 
    unique(by = "entity_name")
}

contact_info <- 
  account %>% 
  left_join(cfo, by = "entity_name") %>% 
  left_join(cao, by = "entity_name") %>% 
  mutate(cfo_name = if_else(is.na(cfo_name), "CFO", cfo_name),
         cao_name = if_else(is.na(cao_name), "CAO", cao_name)) %>% 
  select(entity_name, non_taxing_entity, cfo_name, cao_name, street, city, 
         state, zip, record_type, sf_id, mailing_county, tax_holding_county,
         finet_code) %>% 
  arrange(entity_name)

rm(cao, cfo, account)

if (exists("file_path")) rm(file_path)
```

## Salesforce - Missing Budgets
```{r}
report_budget_year <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT 
      Name AS report_budget_year, 
      Fiscal_Year_Ends__C as fy_end,
      Id
    FROM Report_Year__c
    WHERE IsDeleted = FALSE
    AND Delinquent_Budget__c > 0")

report_budget_year <- report_budget_year %>% 
  mutate(fy_end_month = month(fy_end))


reports__c <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT
      a.Name AS entity_name, 
      Report_Type__c AS missing_report,
      Report_Status__c
    FROM Reports__c AS r
    LEFT JOIN Account AS a
    ON r.Account__c = a.Id
    WHERE r.IsDeleted = FALSE
    AND Delinquent__c = TRUE
    AND r.Report_Type__c IN ('Approved Budget')
    AND r.Entity_Type__c IN (
      SELECT Name
      FROM RecordType
      WHERE Name IN (
        'AOG', 'City', 'Community Reinvestment Agency', 'Conservation District',
        'County', 'District Health', 'Housing', 'Independent/Quasi State Entity',
        'Institution of Higher Education', 'Interlocal', 
        'Local and Special Service District', 'Mental Health', 'Non Profits', 
        'Redevelopment Agency/Project Area', 'School District or Charter School',
        'Town'))
    AND a.Entity_Status__c IN (
      'Current',
      'Delinquent',
      'Suspended',
      'On hold')")

missing_budgets_osa <- 
  reports__c %>% 
  left_join(report_budget_year, by = c("Report_Status__c" = "Id")) %>% 
  unite(missing_report, report_budget_year, missing_report, sep = " ") %>% 
  select(-Report_Status__c)

# The following if statemets are to stop "on hold" or naughty entities from
# getting double reported. Its not a big deal, but essentially it saves brooke a
# few minutes. The idea is that entities may be on either a fiscal year budget
# schedule or they follow the traditional calander year. We do not want to
# report people on the wrong fiscal year, so this code seems to fix that. Though
# this mail merge is still is testing/beta.

if(budget_schedule == "traditional_year"){
  missing_budgets_osa<- missing_budgets_osa %>% 
    filter(fy_end_month==12) %>% 
    select(-fy_end_month, -fy_end)
}

if(budget_schedule == "fiscal_year"){
  missing_budgets_osa<- missing_budgets_osa %>% 
    filter(fy_end_month==6) %>% 
    select(-fy_end_month, -fy_end)
}

missing_budgets_osa <- 
  missing_budgets_osa %>% 
  group_by(missing_report) %>% 
  # See how many reports of each type are missing with summarize():
  summarize(n = n()) %>% 
  rowid_to_column("report_id") %>% 
  select(-n) %>% 
  right_join(missing_budgets_osa, by = "missing_report")

missing_budgets_osa <- 
  missing_budgets_osa %>% 
  spread(report_id, missing_report)

missing_budgets_osa[missing_budgets_osa == ""] <-  NA

# Shift reports to the left:
missing_budgets_osa2 <- 
  as.data.frame(
    t(
      apply(
        missing_budgets_osa, 
        1, 
        function(x){return(c(x[!is.na(x)], x[is.na(x)]))})))

colnames(missing_budgets_osa2) <- colnames(missing_budgets_osa)

missing_budgets_osa <- missing_budgets_osa2

rm(report_budget_year, reports__c, missing_budgets_osa2)



for (j in 2:length(missing_budgets_osa)) {
  
  colnames(missing_budgets_osa)[j] <- paste("Auditor ", j - 1)
  
}
rm(j)

missing_budgets_osa <- 
  missing_budgets_osa %>% 
  remove_empty("cols")

missing_budgets_osa$entity_name <- 
  as.character(missing_budgets_osa$entity_name)

```


## Merge Missing Budget report with Contact Information

```{r}
#join the report with the contact_info table
report_send_budget_notices_osa <- 
  contact_info %>% 
  right_join(missing_budgets_osa, by = "entity_name")

# get rid of any potential duplicates

duplicate_budgets <- duplicated(report_send_budget_notices_osa$entity_name)
report_send_budget_notices_osa <- 
  report_send_budget_notices_osa[!duplicate_budgets, ]

#Export reports:

file_path <-
  "S:/Localgov/LG Compliance/Transparency Compliance/Budget Reports/"

if (notice_type == "ten_day_budget_notice") {
  
    report_send_budget_notices_osa %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), 
                    "_mail_merge_10_day_budget_notice_osa.csv"),
      na = "")
} 
```

# DBMS Disconnection

```{r}
dbDisconnect(odbc_salesforce)
```