---
title: "Invalid Employee Names"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
***
The purpose of this report is to identify local governments that may have reported invalid employee names to Transparency.

### Background

Transparency Board policy requires that local governments submit the name, hourly rate (if not salaried), gender, job title, compensation, and taxable reimbursement summary information for each employee (*Policy #01-01.02*, September 4, 2018 revision). When an employee's information is permanently private, protected, or controlled, however, the local government must replace the employee's name with "Not Provided" and leave the gender field blank. Because the validity of the employee names submitted to Transparency has not yet been tested, Auditor Dougall requested that I review the data.

### Analysis

**Identify Invalid Names**

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message=FALSE}
# Packages & Data Connections
library(knitr)
library(odbc)
library(stringr)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
odbc_sf  <- dbConnect(odbc::odbc(), "Salesforce") 
```

```{sql, connection=odbc_sf, output.var="developer_name"}
SELECT DISTINCT DeveloperName
FROM RecordType
WHERE DeveloperName NOT IN (
 'Chat', 'Community', 'Email', 'Phone', 'Social', 'CPA_Firm', 'Community_User',
 'Educational_Foundation', 'Financial_Institution', 'State_Agency',
 'Justice_Court', 'Non_Profits', 'Subpoena', 'LT_Gov_Document', 'Consolidation', 
 'AUP_Checklist', 'Budget_Checklist', 'LEA_Checklist', 'Large_Entity_Checklist',
 'Small_Entity_Checklist', 'Special_Purpose_Audit')
```

```{sql, connection=odbc_sf, output.var="active_local_govs"}
SELECT Transparency_ID__c AS transparency_id,
       Name               AS sf_entity_name
FROM Account
WHERE RecordTypeId IN (
  SELECT Id
  FROM RecordType
  WHERE DeveloperName IN (
    'AOG', 
    'City',
    'Conservation_District',
    'County', 
    'District_Health',     
    'Housing', 
    'Interlocal', 
    'Local_and_Special_Service_District', 
    'Mental_Health', 
    'Redevelopment_Agency_Project_Area', 
    'School_District_or_Charter_School',
    'Town'))
AND Entity_Status__c IN (
  'Current',
  'On hold',
  'Delinquent',
  'Suspended')
```

```{sql, connection=odbc_sf, output.var="no_employees"}
SELECT Account.Name               AS sf_entity_name,
       Account.Transparency_ID__c AS transparency_id
FROM Account
WHERE Account.Id IN (
  SELECT Transparency_Exemption__c.Account__c
  FROM Transparency_Exemption__c
  WHERE Transparency_Exemption__c.Exemption_Reason__c LIKE 
    '%Reports with another entity%' OR
    Transparency_Exemption__c.Exemption_Reason__c LIKE '%No W-2 Employees%')
```

```{sql, connection=odbc_aws, output.var="govt_lvl"}
SELECT DISTINCT govt_lvl
FROM entity
```

```{sql, connection=odbc_aws, output.var="employee_names"}
SELECT DISTINCT vendor.id   AS employee_id,
                vendor.name AS employee_name,
                entity.id   AS transparency_id,
                entity.name AS entity_name
FROM vendor
LEFT JOIN entity
ON entity.id = vendor.entity_id
WHERE vendor.id IN(
  SELECT vendor_summary.vendor_id
  FROM vendor_summary
  WHERE type = 3)
AND vendor.entity_id IN (
  SELECT id
  FROM entity
  WHERE govt_lvl IN (
    'CITY',
    'COUNTY',
    'HOUSING AUTHORITIES',
    'INTERLOCAL',
    'INDEPENDENT',
    'K12 EDUCATION',
    'LOCAL DISTRICTS'
    'SERVICE DISTRICTS'))
```

```{r}
employee_names <- 
  employee_names %>% 
  as_tibble()

employee_names$employee_id <- 
  as.numeric(employee_names$employee_id)

employee_names$transparency_id <- 
  as.numeric(employee_names$transparency_id)

rm(developer_name, govt_lvl)
```

```{r}
employee_names <- 
  employee_names %>% 
  semi_join(active_local_govs, by = "transparency_id") %>% 
  anti_join(no_employees, by = "transparency_id")

distinct_names <- 
  employee_names %>% 
  distinct(employee_name) %>% 
  arrange(employee_name)

rm(active_local_govs, distinct_names, no_employees)
```

After excluding local governments that are inactive, dissolved, or that do not have employees, I searched the data for names that are blank, contain only numbers, or contain text like "Not Available", "Not Provided," "Unavailable", "NA," and "N/A." I found the following:

* Blank fields.
* Fields containing some variation of "Not Provided."
* Fields containing numbers unaccompanied by a name.

```{r}
invalid_names <- 
  employee_names %>% 
  filter(employee_name == "" |
         str_detect(employee_name, regex("^not ", ignore_case = TRUE)) |
         str_detect(employee_name, "^[0-9]+"))
  
number_of_entities <- 
  invalid_names %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

number_of_not_provided <- 
  invalid_names %>% 
  filter(str_detect(employee_name, regex("^not ", ignore_case = TRUE))) %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

number_of_blank_or_number <- 
  invalid_names %>% 
  filter(employee_name == "" |
         str_detect(employee_name, "^[0-9]+")) %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

distinct_invalid_names <- 
  invalid_names %>% 
  distinct(employee_name)

number_of_distinct_invalid_names <- 
  distinct_invalid_names %>% 
  count() %>% 
  as.numeric()

rm(distinct_invalid_names)
```

By the numbers,

* There are `r number_of_distinct_invalid_names` invalid or potentially invalid names across `r number_of_entities` local governments (including variations of "Not Provided").
* There are `r number_of_blank_or_number` local governments that have reported a blank field or number as the employee name.
* There are `r number_of_not_provided` local governments that have reported a "Not Provided" name.

Per Transparency Board policy, the only valid entry for protected information is "Not Provided." Therefore,

* Blank fields and fields containing only numbers are invalid and local governments should correct that information.
* Local governments with a high percentage of "Not Provided" names should provide a reason for protecting so much information, or correct the names inappropriately identified as protected.

```{r}
rm(number_of_blank_or_number, number_of_distinct_invalid_names, 
   number_of_entities, number_of_not_provided)
```

**Invalid Employee Name Totals, by Entity**

```{r}
total_employees <- 
  employee_names %>% 
  group_by(entity_name) %>% 
  summarise(total_employees = n())

entity_totals <- 
  invalid_names %>% 
  group_by(entity_name) %>% 
  summarise(number_invalid = n()) %>% 
  left_join(total_employees, by = "entity_name") %>% 
  mutate(percent_invalid = (number_invalid / total_employees) * 100) %>% 
  mutate(percent_invalid = round(percent_invalid, digits = 1)) %>% 
  select(entity_name, percent_invalid, number_invalid, total_employees) %>% 
  arrange(desc(percent_invalid), desc(number_invalid)) %>% 
  kable(col.names = c("Entity Name", "% Invalid", "Number Invalid", 
                      "Total Employees"), 
        align = "l") %>% 
  print()
```

**Invalid Employee Names, by Entity, by Invalid Name**

```{r}
name_totals <- 
  invalid_names %>% 
  group_by(entity_name, employee_name) %>% 
  summarise(number_of_entries = n()) %>% 
  left_join(total_employees, by = "entity_name") %>% 
  mutate(percent_invalid = (number_of_entries / total_employees) * 100) %>% 
  mutate(percent_invalid = round(percent_invalid, digits = 1)) %>% 
  select(entity_name, employee_name, percent_invalid, number_of_entries,
         total_employees) %>% 
  arrange(desc(percent_invalid), desc(number_of_entries)) %>% 
  kable(col.names = c("Entity Name", "Employee Name", "% Invalid", 
                      "Number Invalid", "Total Employees"), 
        align = "l") %>% 
  print()
```

**Initial Results and Follow-up**

The initial result of running this report in October 2018 showed the following six local governments reported more than ten percent of their employees with either an invalid name (i.e., a blank field or a number) or a protected name (i.e., "Not Provided"):

* Unified Police District
* Weber Human Services
* Jordan School District
* Canyons School District
* Washington Terrace City
* Academy for Math, Engineering, & Science

The high number of "Not Provided" employee names for Unified Police District was previously identified and addressed by Tyson Plastow during a Special Purpose Audit of the local government (the head of UPD independently determined that the information of all law enforcement personnel under his jurisdiction should be protected, and therefore did not upload employee names). Officials from the remaining five local governments offered the following explanations for their apparently inaccurate information:

* Nate Piggott (Weber Human Services) and Shari' Garrett (Washington Terrace City) said they uploaded incorrect information and would correct it.
* John Larsen (Jordan School District), Leon Wilcox (Canyons School District), and Robert Welch (Academy for Math, Engineering, & Science) said that their LEAs employ a high number of students and that they are legally prohibited from publicly reporting a student's information.

```{r}
dbDisconnect(odbc_aws)
dbDisconnect(odbc_sf)
rm(list = ls())
```