---
title: "Batch Compliance Report"
author: "Michael Jensen"
date: "July 2019"
output: html_notebook
---
# Program Description

**Purpose**

For non-archived Transparency data, identify violations of the following reporting requirements:

* `fiscal_year` is reasonable (i.e., not an archived fiscal year and not a future fiscal year).
* `type` is 1, 2, 3, or 7 for non-State of Utah entities.
* `posting_date` is reasonable (i.e., the posting_date is within the interval of three months prior to the start of the `fiscal_year` value through six months following the end of the `fiscal_year` value).
    + Note: Per a 2019-07 phone conversation with a local government CFO, notifying entities of unreasonable `posting_date` values will result in `posting_date` values that are less transparent and accountable. This is because a CFO is likely to change the incorrect `posting_date` value in the pipe-delimited file he or she uploaded to Transparency in order to become compliant, rather than correct the problem in the entity's accounting software and re-upload the data.
* `account_number` is a code found in the OSA **Uniform Chart of Accounts**, which means:
    + `account_number` is a 17-character string (19-character if the dashes are included in the count).
    + `account_number` contains a valid 3-character fund code.
    + `account_number` contains a valid 6-character function code.
    + `account_number` contains a valid 8-character account code, where the account code is valid for the corresponding transaction type (e.g., a revenue transaction must not have an expense-related account code).

**Input(s)**

* The DSN for the ODBC to AWS.
* The DSN for the ODBC to Salesforce.

```{r}
dsn_aws        <- "transpAWS"
dsn_salesforce <- "Salesforce"
```

**Output(s)**

* A report containing the unique `fiscal_year` values in the non-archived Transparency data (incorrect values would then trigger an investigation of the data).

* A report containing the unique `type` values in the non-archived Transparency data (incorrect values would then trigger an investigation of the data).

* A .csv file listing the entities with `posting_date` and `account_number` violations and a summary of each problem identified.
  + Whether the entity has blank or NA `account_number` values
  + The number of `account_number` values that are not the correct number of characters
  + The number of invalid fund codes
  + The number of invalid function codes
  + The number of invalid expense account codes
  + The number of invalid revenue account codes

* For each entity with `posting_date` violations, a .csv file containing the following information:
  + Entity Salesforce ID
  + Entity name
  + Batch ID
  + File name of the invalid batch
  + Upload date
  + Upload username
  + Transaction types in the batch
  + Beginning transaction date
  + End transaction date
  + File record count
  + File total amount
  + The invalid dates
  
* For each entity with `account_number` violations, a .csv file containing the invalid data for each of the following violations:
  + `account_number` values that are not the correct number of characters
  + Invalid fund codes
  + Invalid function codes used
  + Invalid account codes used

# Libraries and Data Source(s)

```{r}
library(lubridate)
library(magrittr)
library(odbc)
library(readxl)
library(splitstackshape)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_salesforce)

rm(dsn_aws, dsn_salesforce)

download.file(
  "http://financialreports.utah.gov/chartofaccounts/ChartofAccountFull.xlsx",
  "ucoa.xlsx",
  mode = "wb")
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}
  #   batch_id (num): The batch's Transparency ID.
  #   begin_fy (Date): The first day of the entity's fiscal year.
  #   field_name (char): The name of the field to query.
  #   govt_type (char): The type of government (e.g., City).
  #   sf_id (char): The entity's Salesforce ID.
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   trxn_type (num): Transaction type (1 = expense, 2 = revenue).
  #   ucoa (list): The list containing the Fund, Function, and Account codes 
  #     from OSA's Uniform Chart of Accounts.
  #   ucoa_type (char): The UCoA component to check ("funct" = function,
  #     "exp" = expense, "rev" = revenue).
```


## check_posting_date

```{r}
check_posting_date <- function(batch_id, begin_fy) {
  # Check a batch's posting_date values to determine whether they are
  # reasonable.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #   begin_fy (Date): The first day of the entity's fiscal year.
  #
  # Value:
  #   Character.
  #
  # Comments:
  #   We consider the posting_date value to be reasonable if it is within three
  #   month prior to the start of the fiscal_year value through six months
  #   after the end of the fiscal_year value. Three months ahead of the fiscal
  #   year accomodates accounts payable transactions that are billed late and 
  #   six months after the fiscal year matches the Transparency Board policy 
  #   that entities upload year-end corrections within six months of the end of
  #   the fiscal year.
  #
  #   Thus, a posting_date value in the range of October 1, 2017 through
  #   June 30, 2019 is valid if the fiscal_year value is 2018 and the batch is
  #   from an entity with a fiscal year that begins on January 1.

  date_and_fy <- 
    dbGetQuery(
      odbc_aws,
      paste("
            SELECT DISTINCT posting_date, fiscal_year
            FROM transaction
            WHERE batch_id = ", batch_id)) %>% 
    mutate(fiscal_year = as.numeric(.[["fiscal_year"]]),
           begin_fy    = !!begin_fy)
  
  # Ensure begin_fy matches fiscal_year:
  if (month(begin_fy) == 1) {
    
    year(date_and_fy$begin_fy) <- date_and_fy$fiscal_year
    
  } else {
    
    year(date_and_fy$begin_fy) <- date_and_fy$fiscal_year - 1
  }
  
  date_and_fy$interval <- 
    (date_and_fy$begin_fy - months(3)) %--% 
    (date_and_fy$begin_fy + months(18) - 1)
  
  if (all(date_and_fy$posting_date %within% date_and_fy$interval)) {
    
    ""
    
  } else {
    
    date_and_fy %>% 
      filter(!posting_date %within% interval) %>% 
      .[["posting_date"]] %>% 
      paste(collapse = ", ")
  }
}
```

## check_ucoa

```{r}
check_ucoa <- function(batch_id, govt_type, ucoa) {
  # Check whether a batch has valid Uniform Chart of Accounts codes.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #   govt_type (char): The type of government (e.g., City).
  #   ucoa (list): The list containing OSA's Uniform Chart of Accounts Fund,
  #     Function, and Account codes.
  #
  # Value:
  #   Tibble.
  #
  # Comments:
  #   Because type 3 (payroll) information is not required to have a UCoA code
  #   and we do not require entities to upload type 7 (balance sheet)
  #   information, I decided to exlude those transaction types here.
  
  ucoa_reported <-
    dbGetQuery(
      odbc_aws,
      paste("
            SELECT DISTINCT type, account_number
            FROM transaction
            WHERE batch_id = ", batch_id, "
            AND type IN (1, 2)")) %>%
    as_tibble()

  invalid_ucoa_info <- 
    tibble(
      batch_id            = batch_id,
      any_blank_or_na     = NA,
      not_19_char         = NA,
      invalid_fund        = NA,
      invalid_funct       = NA,
      invalid_account_exp = NA,
      invalid_account_rev = NA)
  
  if (govt_type == "School_District_or_Charter_School") {
    
    return(invalid_ucoa_info)
  }
  
  if (any(is.na(ucoa_reported$account_number)) || 
      any(ucoa_reported$account_number == "")) {

    invalid_ucoa_info$any_blank_or_na <- "Yes"
    
    ucoa_reported <- 
      ucoa_reported %>% 
      filter(account_number != "", !is.na(account_number))
    
  }
  
  if (any(nchar(ucoa_reported$account_number) != 19)) {
    
    invalid_ucoa_info$not_19_char <- 
      ucoa_reported %>% 
      filter(nchar(account_number) != 19) %>% 
      .[["account_number"]] %>% 
      paste(collapse = ", ") %>% 
      sort()
    
    ucoa_reported <- 
      ucoa_reported %>% 
      filter(nchar(account_number) == 19)
  }
  
  fund <- 
    ucoa_reported %>% 
    .[["account_number"]] %>% 
    substring(1, 3)
  
  funct <-
    ucoa_reported %>% 
    .[["account_number"]] %>% 
    substring(5, 10)
  
  account <- 
    ucoa_reported %>% 
    mutate(account_number = substring(account_number, 12, 19))
  
  account_exp <- 
    account %>% 
    filter(type == 1) %>% 
    .[["account_number"]]
    
  account_rev <- 
    account %>%
    filter(type == 2) %>% 
    .[["account_number"]]
  
  if (!all(fund %in% ucoa[["fund"]][["NUMBER"]])) {
    
    invalid_ucoa_info$invalid_fund <- 
      fund[!fund %in% ucoa[["fund"]][["NUMBER"]]] %>% 
      unique() %>% 
      paste(collapse = ", ") %>% 
      sort()
  }
  
  if (!all(funct %in% ucoa[["funct"]][["NUMBER"]])) {
    
    invalid_ucoa_info$invalid_funct <- 
      funct[!funct %in% ucoa[["funct"]][["NUMBER"]]] %>% 
      unique() %>% 
      paste(collapse = ", ") %>%
      sort()
  }
  
  if (!all(account_exp %in% ucoa[["account_exp"]][["NUMBER"]])) {
    
    invalid_ucoa_info$invalid_account_exp <- 
      account_exp[!account_exp %in% ucoa[["account_exp"]][["NUMBER"]]] %>% 
      unique() %>%
      paste(collapse = ", ") %>%
      sort()
  }
  
  if (!all(account_rev %in% ucoa[["account_rev"]][["NUMBER"]])) {
    
    invalid_ucoa_info$invalid_account_rev <- 
      account_rev[!account_rev %in% ucoa[["account_rev"]][["NUMBER"]]] %>% 
      unique() %>%
      paste(collapse = ", ") %>% 
      sort()
  }
  
  invalid_ucoa_info
}
```

## generate_report

```{r}
generate_report <- function(t_id, begin_fy, govt_type, name, sf_id, ucoa) {
  # Generate the batch compliance report for an entity.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   begin_fy (Date): The first day of the entity's fiscal year.
  #   govt_type (char): The type of government (e.g., City).
  #   name: The entity's name.
  #   sf_id: The entity's Salesforce ID.
  #   ucoa (list): The list containing OSA's Uniform Chart of Accounts Fund,
  #     Function, and Account codes.
  #
  # Value:
  #   Tibble.
  
  batch_ids <- 
    query_batch_ids(t_id)
  
  # Why am I creating an empty row of data if there are no batch IDs?
  # Did I do this because I can't skip those entities?
  if (length(batch_ids) == 0 || nrow(batch_ids) == 0) {
    
    report <-
      tibble(
        batch_id             = NA,
        fiscal_year          = NA,
        any_blank_or_na      = NA,
        not_19_char          = NA,
        invalid_fund         = NA,
        invalid_funct        = NA,
        invalid_account_exp  = NA,
        invalid_account_rev  = NA,
        invalid_date         = NA,
        entity_name          = NA,
        sf_id                = NA,
        upload_date          = NA,
        begin_txn_date       = NA,
        end_txn_date         = NA,
        transaction_type     = NA,
        username             = NA,
        uploaded_file        = NA,
        file_record_count    = NA,
        file_total_amount    = NA)
    
    return(report)
  }
  
  report <-
    batch_ids$batch_id %>% 
    map(check_ucoa, govt_type, ucoa) %>% 
    bind_rows()   %>% 
    mutate(invalid_date = map(batch_id, check_posting_date, begin_fy),
           entity_name  = !!name,
           sf_id        = !!sf_id) %>% 
    unnest(invalid_date)
  
  report <- 
    report %>% 
    mutate(
      transaction_type    = map(batch_id, query_type),
      upload_date         = map(batch_id, query_date_field, "upload_date"),
      begin_txn_date      = map(batch_id, query_date_field, "begin_txn_date"),
      end_txn_date        = map(batch_id, query_date_field, "end_txn_date"),
      username            = map(batch_id, query_username),
      uploaded_file       = map(batch_id, query_file_name),
      file_record_count   = map(batch_id, 
                                query_batch_field, 
                                "file_record_count"),
      file_total_amount   = map(batch_id, 
                                query_batch_field, 
                                "file_total_amount"),
      entity_name         = name,
      entity_id           = sf_id,
      fiscal_year         = map(batch_id, query_fiscal_year)) %>%
    unnest(upload_date, begin_txn_date, end_txn_date, transaction_type,
           username, uploaded_file, file_record_count, file_total_amount) %>% 
    unnest(fiscal_year)
}
```

## query_batch_ids

```{r}
query_batch_ids <- function(t_id) {
  # Query an entity's processed batch IDs.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #
  # Value:
  #   Tibble.
  #
  # Comments:
  #   The 'DONTDELETE' batch status is a variation of 'PROCESSED.' DONTDELETE 
  #   indicates the data in the batch has been split among multiple transaction
  #   tables, as the batch contains data from a fiscal year that has been 
  #   archived.
  
  if (is.na(t_id)) {
    
    return(vector(mode = "numeric", length = 0)) 
  }
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT id
          FROM batch
          WHERE entity_id = ", t_id, "
          AND status IN ('PROCESSED', 'DONTDELETE')")) %>% 
    as_tibble() %>% 
    rename("batch_id" = "id")
}
```


## query_date_field

```{r}
query_date_field <- function(batch_id, field_name) {
  # Query one of a batch's date fields (e.g., upload_date).
  #
  # Arguments:
  #   field_name (char): The name of the field to query.
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Date.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT ", field_name, " AS date_field
          FROM batch
          WHERE id = ", batch_id)) %>%
    .[["date_field"]] %>% 
    as.Date()
}
```

## query_file_name

```{r}
query_file_name <- function(batch_id) {
  # Query the file name of an uploaded batch.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Character.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT upload_file
          FROM batch
          WHERE id = ", batch_id)) %>%
    .[["upload_file"]]
}
```

## query_fiscal_year

```{r}
query_fiscal_year <- function(batch_id) {
  # Query the fiscal year of a batch.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Numeric.

  dbGetQuery(
    odbc_aws,
    paste("
          SELECT DISTINCT fiscal_year
          FROM transaction
          WHERE batch_id = ", batch_id)) %>% 
    .[["fiscal_year"]] %>% 
    as.numeric()
}
```

## query_type

```{r}
query_type <- function(batch_id) {
  # Query the transaction types contained in a batch.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Character.
  
  reported_types <- 
    dbGetQuery(
      odbc_aws,
      paste("
            SELECT DISTINCT type
            FROM transaction
            WHERE batch_id = ", batch_id))
  
  reported_types$name <- 
    if_else(
      reported_types$type == 1,
      "EXP",
      if_else(
        reported_types$type == 2,
        "REV",
        if_else(
          reported_types$type == 3,
          "PAYROLL",                  # I decided not to check PAYROLL data, so
          if_else(                    # this won't appear in the report.
            reported_types$type == 7,
            "BS",                     # I decided not to check BS data, so this 
                                      # won't appear in the report.
            "OTHER"))))
  
  reported_types$name %>% 
    paste(collapse = ", ")
}
```

## query_batch_field

```{r}
query_batch_field <- function(batch_id, field_name) {
  # Query a non-date field from the Batch Table.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #   field_name (char): The name of the field to query.
  #
  # Value:
  #   Character or numeric.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT ", field_name, " AS field_name
          FROM batch
          WHERE id = ", batch_id)) %>% 
    .[["field_name"]]
}
```

## query_username

```{r}
query_username <- function(batch_id) {
  # Query the username of the person who uploaded a batch.
  #
  # Arguments:
  #   batch_id (num): The batch's Transparency ID.
  #
  # Value:
  #   Character.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT upload_username
          FROM batch
          WHERE id = ", batch_id)) %>%
    .[["upload_username"]]
}
```

# Execution

## Salesforce

```{r}
sf_data <-
  dbGetQuery(
    odbc_sf,
    paste("
          SELECT
            Account.Name                  AS name,
            Account.Id                    AS id,
            Account.Transparency_ID__c    AS t_id,
            Account.Fiscal_Year_Begins__c AS begin_fy,
            RecordType.DeveloperName      AS govt_type
          FROM Account
          JOIN RecordType
          ON Account.RecordTypeId = RecordType.Id
          WHERE Account.RecordTypeId IN (
            SELECT Id
            FROM RecordType
            WHERE DeveloperName IN (
              'AOG',
              'City',
              'Conservation_District',
              'County',
              'District_Health',
              'Housing',
              'Independent_Quasi_State_Entity',
              'Interlocal',
              'Local_and_Special_Service_District',
              'Mental_Health',
              'Redevelopment_Agency_Project_Area',
              'School_District_or_Charter_School',
              'Town'))
          AND Account.Entity_Status__c IN (
            'Current',
            'On hold',
            'Delinquent',
            'Suspended')
          AND Account.Name NOT IN (
            'Intermountain Power Agency',
            'Utah Associated Municipal Power Systems',
            'Utah Municipal Power Agency')
          AND (
            Account.Expense_Revenue_Start_Date__c <= DATE() OR
            Account.Expense_Revenue_Start_Date__c IS NULL)")) %>%
  as_tibble()
```

## UCoA

```{r}
ucoa_fund <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[1]])

ucoa_function <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[2]])

ucoa_account <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[3]])

# Some of the code below will become unnecessary after I edit OSA's Uniform
# Chart of Accounts and publish it on the OSA website.

colnames(ucoa_fund)     <- ucoa_fund[2, ]
colnames(ucoa_function) <- c("NUMBER", ucoa_function[1, 2:4])
colnames(ucoa_account)  <- ucoa_account[2, ]

ucoa_fund     <- ucoa_fund %>% slice(-1, -2)
ucoa_function <- ucoa_function %>% slice(-1)
ucoa_account  <- ucoa_account %>% slice(-1, -2)

extra_fund_numbers <- 
  c(202:298, 302:398, 402:448, 452:498, 502:598, 602:698, 702:798) %>% 
  as.character() %>% 
  enframe(name = NULL) %>% 
  rename("NUMBER" = "value") %>% 
  mutate("SHORT DESCRIPTION" = NA, "FULL DESCRIPTION" = NA, "DETAIL" = NA)

ucoa_fund <- 
  ucoa_fund %>% 
  bind_rows(extra_fund_numbers)

ucoa_fund$NUMBER[[1]]     <- "010"
ucoa_fund$NUMBER[[2]]     <- "020"
ucoa_fund$NUMBER[[3]]     <- "030"
ucoa_function$NUMBER[[1]] <- "000000"

ucoa_account_exp <-
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^4"))

ucoa_account_rev <- 
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^3"))
  
# ucoa_account_w2 <- 
#   ucoa_account %>% 
#   filter(str_detect(NUMBER, "^4001"))

ucoa <-
  list(
    fund        = ucoa_fund,
    funct       = ucoa_function,
    account     = ucoa_account,
    account_exp = ucoa_account_exp,
    account_rev = ucoa_account_rev)

rm(ucoa_fund, ucoa_function, ucoa_account, extra_fund_numbers, ucoa_account_exp,
   ucoa_account_rev)
```

## Reports

### Invalid `fiscal_year` and `type`

```{r}
entity_ids <- 
  dbGetQuery(odbc_aws, "SELECT id, name FROM entity")

# Check fiscal_year:
report_invalid_fy <- 
  dbGetQuery(
    odbc_aws,
    "
    SELECT DISTINCT batch_id, fiscal_year, batch.entity_id
    FROM transaction
    JOIN batch
    ON transaction.batch_id = batch.id
    WHERE fiscal_year NOT IN (2014, 2015, 2016, 2017, 2018, 2019, 2020)")

if (nrow(report_invalid_fy) > 0) {
  
  report_invalid_fy <- 
    report_invalid_fy %>% 
    left_join(entity_ids, by = c("entity_id" = "id")) %>% 
    select(entity_name = name, entity_id, batch_id, fiscal_year) %>% 
    arrange(entity_name)
  
  report_invalid_fy <- 
    report_invalid_fy$batch_id %>% 
    map(
      ~ dbGetQuery(
        odbc_aws,
        paste("
          SELECT 
            batch.id AS batch_id, upload_date, upload_username, upload_file
          FROM batch
          WHERE batch.id = ", .x))) %>% 
    bind_rows() %>% 
    left_join(report_invalid_fy, by = "batch_id") %>% 
    select(entity_name, entity_id, batch_id, fiscal_year, upload_date,
           upload_username, upload_file)
}

# Check type (type 7 is technically valid, but so unreliable we've asked 
# entities to stop reporting it, which is why I've excluded it here):
report_invalid_type <- 
  dbGetQuery(
    odbc_aws,
    "
    SELECT DISTINCT
      batch.entity_id,
      transaction.batch_id,
      transaction.type
    FROM transaction
    JOIN batch
    ON batch.id = transaction.batch_id
    WHERE transaction.type NOT IN (1, 2, 3)
    AND batch.entity_id <> 1")

if (nrow(report_invalid_type) > 0) {
  
  report_invalid_type <- 
    report_invalid_type %>% 
    left_join(entity_ids, by = c("entity_id" = "id")) %>% 
    select(entity_name = name, entity_id, batch_id, type) %>% 
    arrange(entity_name)
  
  report_invalid_type <- 
    report_invalid_type$batch %>% 
    map(
      ~ dbGetQuery(
        odbc_aws,
        paste("
          SELECT 
            batch.id AS batch_id, upload_date, upload_username, upload_file
          FROM batch
          WHERE batch.id = ", .x))) %>% 
    bind_rows() %>% 
    left_join(report_invalid_type, by = "batch_id") %>% 
    select(entity_name, entity_id, batch_id, type, upload_date, upload_username,
           upload_file) %>% 
    arrange(type)
}

rm(entity_ids)
```

### Invalid 'posting_date` and `account_number`

```{r}
# sf_data <- 
#   sf_data %>% 
#   filter(!is.na(t_id)) %>% 
#   filter(t_id == 445 | # Highland City
#          t_id == 299 | # Box Elder County
#          t_id == 631 | # West Valley City
#          t_id == 605 | # Tooele City
#          t_id == 919)  # Stansbury Service Agency

sf_data <- 
  sf_data %>% 
  filter(!is.na(t_id))

entity_batches <- 
  list(
    t_id      = as.list(sf_data$t_id),
    begin_fy  = as.list(sf_data$begin_fy),
    govt_type = as.list(sf_data$govt_type),
    name      = as.list(sf_data$name),
    sf_id     = as.list(sf_data$id)) %>% 
  pmap(generate_report, ucoa)

names(entity_batches) <- sf_data$name

entity_batches_invalid <- 
  entity_batches %>% 
  bind_rows() %>%
  select(entity_name, entity_id, batch_id, fiscal_year, 
         any_blank_or_na, not_19_char, invalid_fund, invalid_funct,
         invalid_account_exp, invalid_account_rev, invalid_date,
         username, uploaded_file, upload_date, transaction_type,
         begin_txn_date, end_txn_date, file_record_count, 
         file_total_amount) %>%
  filter(!is.na(any_blank_or_na)     |
         !is.na(not_19_char)         |
         !is.na(invalid_fund)        |
         !is.na(invalid_funct)       |
         !is.na(invalid_account_exp) |
         !is.na(invalid_account_rev) |
         invalid_date != "") %>% 
  arrange(entity_name, fiscal_year)
```

### Summary Report

```{r}
report_summary <- 
  sf_data %>% 
  select(entity_name = name, t_id, govt_type) %>% 
  mutate(
    any_blank_or_na            = NA,
    number_not_19_char         = NA,
    number_invalid_fund        = NA,
    number_invalid_function    = NA,
    number_invalid_account_exp = NA,
    number_invalid_account_rev = NA)

for (i in 1:nrow(report_summary)) {
  
  a <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(any_blank_or_na)
  
  if (any(!is.na(a))) {
    
    report_summary$any_blank_or_na[[i]] <- "Yes"
    
  } 
  rm(a)
}
rm(i)

for (i in 1:nrow(report_summary)) {
  
  report_summary$number_not_19_char[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(not_19_char) %>% 
    filter(!is.na(not_19_char)) %>% 
    cSplit(
      splitCols = "not_19_char", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique() %>% 
    nrow()
}
rm(i)

for (i in 1:nrow(report_summary)) {
  
  report_summary$number_invalid_fund[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(invalid_fund) %>% 
    filter(!is.na(invalid_fund)) %>% 
    cSplit(
      splitCols = "invalid_fund", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique() %>% 
    nrow()
}
rm(i)

for (i in 1:nrow(report_summary)) {
  
  report_summary$number_invalid_function[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(invalid_funct) %>% 
    filter(!is.na(invalid_funct)) %>% 
    cSplit(
      splitCols = "invalid_funct", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique() %>% 
    nrow()
}
rm(i)

for (i in 1:nrow(report_summary)) {
  
  report_summary$number_invalid_account_exp[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(invalid_account_exp) %>% 
    filter(!is.na(invalid_account_exp)) %>% 
    cSplit(
      splitCols = "invalid_account_exp", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique() %>% 
    nrow()
}
rm(i)

for (i in 1:nrow(report_summary)) {
  
  report_summary$number_invalid_account_rev[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(invalid_account_rev) %>% 
    filter(!is.na(invalid_account_rev)) %>% 
    cSplit(
      splitCols = "invalid_account_rev", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique() %>% 
    nrow()
}
rm(i)

report_summary <- 
  report_summary %>% 
  filter(!is.na(t_id)) %>% 
  filter(!is.na(any_blank_or_na)         |
         number_not_19_char         != 0 |
         number_invalid_fund        != 0 |
         number_invalid_function    != 0 |
         number_invalid_account_exp != 0 |
         number_invalid_account_rev != 0)
```

```{r}
file_path <-
  "S:/Localgov/LG Compliance/Transparency Compliance/Compliance Reports/"

report_summary %>%
  write_csv(
    path = paste0(file_path, Sys.Date(), " Batch Compliance Report.csv"),
    na = "")

report_invalid_fy %>%
  write_csv(
    path = paste0(file_path, Sys.Date(), " Invalid FY Report.csv"),
    na = "")

report_invalid_type %>%
  write_csv(
    path = paste0(file_path, Sys.Date(), " Invalid Type Report.csv"),
    na = "")
```

## Individual Files for Invalid Data

*Note: As of 2019-07-30, Excel will round the numbers in the .csv files. Use Notepad or some other application instead when viewing the data.*

Not 19-characters:

```{r}
list_not_19_char <- list()

for (i in 1:nrow(report_summary)) {

  list_not_19_char[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(not_19_char) %>% 
    filter(!is.na(not_19_char)) %>% 
    cSplit(
      splitCols = "not_19_char", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_not_19_char) <- report_summary$entity_name

for (i in names(list_not_19_char)) {
  
  if (nrow(list_not_19_char[[i]]) > 0) {
    
   write_csv(list_not_19_char[[i]], paste0(i, "_not_19_chars.csv")) 
  }
}
rm(i)
```

Number Invalid Fund:

```{r}
list_invalid_fund <- list()

for (i in 1:nrow(report_summary)) {

  list_invalid_fund[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(invalid_fund) %>% 
    filter(!is.na(invalid_fund)) %>% 
    cSplit(
      splitCols = "invalid_fund", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_invalid_fund) <- report_summary$entity_name

for (i in names(list_invalid_fund)) {
  
  if (nrow(list_invalid_fund[[i]]) > 0) {
    
   write_csv(list_invalid_fund[[i]], paste0(i, "_invalid_fund.csv")) 
  }
}
rm(i)
```

Number Invalid Function:

```{r}
list_invalid_funct <- list()

for (i in 1:nrow(report_summary)) {

  list_invalid_funct[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(invalid_funct) %>% 
    filter(!is.na(invalid_funct)) %>% 
    cSplit(
      splitCols = "invalid_funct", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_invalid_funct) <- report_summary$entity_name

for (i in names(list_invalid_funct)) {
  
  if (nrow(list_invalid_funct[[i]]) > 0) {
    
   write_csv(list_invalid_funct[[i]], paste0(i, "_invalid_function.csv")) 
  }
}
rm(i)
```

Number Invalid Account Exp:

```{r}
list_invalid_account_exp <- list()

for (i in 1:nrow(report_summary)) {

  list_invalid_account_exp[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(invalid_account_exp) %>% 
    filter(!is.na(invalid_account_exp)) %>% 
    cSplit(
      splitCols = "invalid_account_exp", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_invalid_account_exp) <- report_summary$entity_name

for (i in names(list_invalid_account_exp)) {
  
  if (nrow(list_invalid_account_exp[[i]]) > 0) {
    
   write_csv(list_invalid_account_exp[[i]], paste0(i, "_invalid_account_exp.csv")) 
  }
}
rm(i)
```

Number Invalid Account Rev:

```{r}
list_invalid_account_rev <- list()

for (i in 1:nrow(report_summary)) {

  list_invalid_account_rev[[i]] <- 
    entity_batches_invalid %>% 
    filter(entity_name == report_summary$entity_name[[i]]) %>% 
    select(invalid_account_rev) %>% 
    filter(!is.na(invalid_account_rev)) %>% 
    cSplit(
      splitCols = "invalid_account_rev", 
      sep = ",", 
      direction = "long",
      type.convert = FALSE) %>%  
    unique()
}
rm(i)

names(list_invalid_account_rev) <- report_summary$entity_name

for (i in names(list_invalid_account_rev)) {
  
  if (nrow(list_invalid_account_rev[[i]]) > 0) {
    
   write_csv(list_invalid_account_rev[[i]], paste0(i, "_invalid_account_rev.csv")) 
  }
}
rm(i)
```

# DBMS Disconnection

```{r}
dbDisconnect()
```