---
title: "Identify Invalid Payee/Customer/Vendor Names"
author: "Michael Jensen"
output: html_notebook
---
# Program Description

**Purpose**

Identify the entities that have reported invalid or potentially invalid payee/customer/vendor names to Transparent Utah.

**Input(s)**

```{r}
dsn_aws        <- "transpAWS"
dsn_salesforce <- "Salesforce"

# Input the most recently archived fiscal year:
most_recent_archived_fy <- 2013
```

**Output(s)**

1) A .csv file containing the following information for each active and participating entity:

* Entity name
* Entity Salesforce ID
* Percentage of expense transactions with a P/C/V name of "Not Applicable"
* Percentage of expense transactions with a P/C/V name of "Not Provided"
* Percentage of expense transactions with a P/C/V name of that appears to be invalid
* Percentage of revenue transactions with a P/C/V name of "Not Applicable"
* Percentage of revenue transactions with a P/C/V name of "Not Provided"
* Percentage of revenue transactions with a P/C/V name of that appears to be invalid

2) A report for both expense and revenue transactions that an analyst can use to browse for meaningful information.

**Comments**

Local governments must report the name of the payee, customer, or vendor for each transaction reported to Transparent Utah, with two exceptions (*State of Utah Transparency Website File Layout*, 28 August 2013):

* When the transaction does not have a payee, customer, or vendor (e.g., a journal voucher entry), report "Not Applicable."
* When the payee, customer, or vendor's information is protected and will always remain protected (e.g., protected by GRAMA, HIPPA, or FERPA), report "Not Provided."

In instances where the payee, customer, or vendor's information is protected but may become unprotected in the future (e.g., an undercover officer or an employee with a protective order), local governments must report the information and indicate it is temporarily protected. They do so by reporting a "P" in the Protection Indicator Field of the file they upload to Transparent Utah, which will mask the name, Doing Business As name, and gender of the temporarily protected person.

# Libraries and Data Sources

```{r}
library(odbc)
library(stringr)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_salesforce)
rm(dsn_aws, dsn_salesforce)
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}
  #   most_recent_archived_fy (num): The most recently archived fiscal year,
  #     defined in the "Input(s)" section of this R program.
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   total_record_count (num): The number of non-archived expense or revenue
  #     transactions an entity has reported to Transparent Utah.
  #   trxn_type (num): Transaction type (1 = expense, 2 = revenue).
```

## count_records()

```{r}
count_records <- function(t_id, trxn_type) {
  # Determine the number of non-archived expense or revenue transactions an
  # entity has reported to Transparent Utah.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   trxn_type (num): Transaction type (1 = expense, 2 = revenue).
  #
  # Value:
  #   Numeric.

  if (is.na(t_id)) {
    
    return(NA)
  }

  dbGetQuery(
    odbc_aws,
    paste("
      SELECT COUNT(id) AS record_count
      FROM transaction
      WHERE type = ", trxn_type, "
      AND batch_id IN (
        SELECT id
        FROM batch
        WHERE entity_id = ", t_id, ")")) %>% 
  .$record_count %>% 
  as.numeric()
}
```

## count_vendors()

```{r}
count_vendors <- function(t_id, trxn_type) {
  # Determine the total number of vendors an entity has for expense or revenue
  # transactions, for non-archived fiscal years.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   trxn_type (num): Transaction type (1 = expense, 2 = revenue).
  #
  # Value:
  #   Numeric.
  #
  # Comments:
  #   Entities with a high or low number of vendors may not be correctly
  #   reporting vendor information to Transparent Utah.
  
  if (is.na(t_id)) {
    
    return(NA)
  }
  
  dbGetQuery(
      odbc_aws,
      paste("
        SELECT vendor_id
        FROM vendor_summary
        WHERE fiscal_year > ", most_recent_archived_fy, "
        AND type = ", trxn_type, "
        AND entity_id = ", t_id)) %>% 
   distinct(vendor_id) %>% 
   nrow() %>% 
   as.numeric()
}
```

## perc_of_total()

```{r}
perc_of_total <- function(t_id, total_record_count, trxn_type) {
  # Determine the vendor-to-total transaction percentage.
  # 
  # Arguments:
  #   most_recent_archived_fy (num): The most recently archived fiscal year,
  #     defined in the "Input(s)" section of this R program.
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   total_record_count (num): The number of non-archived expense or revenue
  #     transactions an entity has reported to Transparent Utah.
  #   trxn_type (num): Transaction type (1 = expense, 2 = revenue).
  #
  # Value:
  #   Numeric.
  
  if (is.na(t_id) || total_record_count == 0) {
    
    return(
      tibble())
  }
  
  vendor <- 
    dbGetQuery(
      odbc_aws,
      paste("
        SELECT 
          entity.name AS entity_name,
          vendor.name AS vendor_name, 
          vendor.id   AS vendor_id
        FROM vendor
        LEFT JOIN entity
        ON vendor.entity_id = entity.id
        WHERE entity_id = ", t_id))
  
  vendor_summary <- 
    dbGetQuery(
      odbc_aws,
      paste("
        SELECT vendor_id, count
        FROM vendor_summary
        WHERE fiscal_year > ", most_recent_archived_fy, "
        AND type = ", trxn_type, "
        AND entity_id = ", t_id)) %>% 
    group_by(vendor_id) %>% 
    summarize(record_count = sum(count)) %>% 
    left_join(vendor, by = "vendor_id") %>% 
    select(entity_name, vendor_name, vendor_id, record_count)

  vendor_summary %>% 
    mutate(
      percent = 
        round((record_count / total_record_count) * 100, digits = 2)) %>% 
    # filter(percent >= 5.0) %>% 
    arrange(desc(percent))
}
```

# Execution

## Salesforce

Import active and participating entities:

```{r}
sf_data <-
  dbGetQuery(
    odbc_sf,
    paste("
          SELECT
            Account.Name                  AS entity_name,
            Account.Id                    AS sf_id,
            Account.Transparency_ID__c    AS t_id
            -- RecordType.DeveloperName   AS govt_type
          FROM Account
          JOIN RecordType
          ON Account.RecordTypeId = RecordType.Id
          WHERE Account.RecordTypeId IN (
            SELECT Id
            FROM RecordType
            WHERE DeveloperName IN (
              'AOG',
              'City',
              'Community_Reinvestment_Agency',
              'Conservation_District',
              'County',
              'District_Health',
              'Housing',
              'Independent_Quasi_State_Entity',
              'Institute_of_Higher_Education',
              'Interlocal',
              'Justice_Court',
              'Local_and_Special_Service_District',
              'Mental_Health',
              'Redevelopment_Agency_Project_Area',
              'School_District_or_Charter_School',
              'Town'))
          AND Account.Entity_Status__c IN (
            'Current',
            'On hold',
            'Delinquent',
            'Suspended')
          AND Account.Name NOT IN (
            'Intermountain Power Agency',
            'Utah Associated Municipal Power Systems',
            'Utah Municipal Power Agency')
          AND (
            Account.Wage_Start_Date__c <= DATE() OR
            Account.Wage_Start_Date__c IS NULL)
          ORDER BY Account.Name")) %>%
  as_tibble()
```

## Transparent Utah - Vendor-to-Total Ratio

I think a more useful metric would be the dollar values, rather than percentage of transactions. It will be more easy to grasp the scope of the problem when conveyed in dollars.

```{r}
invalid_names <- 
  sf_data %>% 
  mutate(
    record_count_exp = map_dbl(t_id, count_records, trxn_type = 1),
    record_count_rev = map_dbl(t_id, count_records, trxn_type = 2))

high_perc_exp <- 
  pmap(
    list(
      t_id               = as.list(invalid_names$t_id),
      total_record_count = as.list(invalid_names$record_count_exp)),
    perc_of_total,
    trxn_type = 1) %>% 
  bind_rows() %>% 
  arrange(desc(percent))

high_perc_rev <- 
  pmap(
    list(
      t_id               = as.list(invalid_names$t_id),
      total_record_count = as.list(invalid_names$record_count_rev)),
    perc_of_total,
    trxn_type = 2) %>% 
  bind_rows() %>% 
  arrange(desc(percent))
```

## Transparent Utah - Granite SD-like problems

The problem with Granite SD's data is that the "SCH VENDOR ID: 123456" and "VENDOR ID: 123456" transactions are just above 0% of the LEA's total transactions.

```{r}
problem_names <- 
  sf_data %>% 
  filter(t_id == 57) %>% 
  mutate(
    record_count_exp = map_dbl(t_id, count_records, trxn_type = 1),
    record_count_rev = map_dbl(t_id, count_records, trxn_type = 2))

high_perc_exp <- 
  pmap(
    list(
      t_id               = as.list(problem_names$t_id),
      total_record_count = as.list(problem_names$record_count_exp)),
    perc_of_total,
    trxn_type = 1) %>% 
  bind_rows() %>% 
  arrange(desc(percent))

high_perc_rev <- 
  pmap(
    list(
      t_id               = as.list(problem_names$t_id),
      total_record_count = as.list(problem_names$record_count_rev)),
    perc_of_total,
    trxn_type = 2) %>% 
  bind_rows() %>% 
  arrange(desc(percent))
```

```{r}


total_vendors <- 
  sf_data %>% 
  mutate(total_vendors_exp = 
           map_dbl(t_id, count_vendors, 1))
```

## Definitely Invalid Names

Perhaps I need to tackle this problem from multiple angles.

* A report of entities with a vendor having a total percentage of transactions greater than x%.
* A report of the entities with a high total number of vendors.
* A report of the entities with PCV names that we have determine are invalid or are likely invalid (this report would be similar to the first draft of the code)

### Definitely Invalid Names - old code

#### Identify Valid and Invalid Names

```{r}
exp_names <- 
  as_tibble(exp_names)

rev_names <- 
  as_tibble(rev_names)

entity_table$id <- 
  as.integer(entity_table$id)

exp_names$entity_id <- 
  as.integer(exp_names$entity_id)

exp_names$vendor_id <- 
  as.integer(exp_names$vendor_id)

rev_names$entity_id <- 
  as.integer(rev_names$entity_id)

rev_names$vendor_id <- 
  as.integer(rev_names$vendor_id)

exp_names <- 
  exp_names %>% 
  left_join(entity_table,
            by = c("entity_id" = "id")) %>% 
  select(entity_id, entity_name = name, vendor_id, vendor_name) %>% 
  semi_join(sf_active_local_govs,
            by = c("entity_id" = "transparency_id"))

rev_names <- 
  rev_names %>% 
  left_join(entity_table,
            by = c("entity_id" = "id")) %>% 
  select(entity_id, entity_name = name, vendor_id, vendor_name) %>% 
  semi_join(sf_active_local_govs,
            by = c("entity_id" = "transparency_id"))

rm(aws_entity_types, sf_active_local_govs, entity_table)
```

```{r, eval=FALSE}
exp_distinct_names <- 
  exp_names %>% 
  distinct(vendor_name) %>% 
  arrange(vendor_name)

rev_distinct_names <- 
  rev_names %>% 
  distinct(vendor_name) %>% 
  arrange(vendor_name)

# rm(exp_distinct_names, rev_distinct_names)
```

I searched the names and found the following (as of October 2018):

* "Not Applicable"
* Blank fields
* "% VENDOR ID%" (Granite SD, 2019-09-11)


'"DONT USE"" use #20425"
"-USE VENDOR #2641"
***USE VENDOR #22058***
****DO NOT USE** USE 23559
***DO NOT USE*** SEE V011273 SANDYS FINE FOD
.
....
???
  _____________________
____________________________________
Like "#N/A"
Names surrounded with ""
Names preceeded by "~"
Number/numbers
* 0
* 1.24.18
* 105126
numbers and names (some of which make sense and some of which do not)
* 100594 TODD WOFFINDEN 65938
* 102152 RMFMA 62287
* 102164 ICC 63124
Vendor names containing information that appears like it belongs in an org, cat, or fund column:
  * "0030 Athletics"
* "0050 General"
* "02 sales tax bonds"
* "10.6Elem750"
* "10.6Misc3975"

Non-sensicals that include a date, transaction number (?), and a city
* "01/04 509655EX 665646 11.8 BLUFF"
* "01/11 Workers Compensation accrual"


```{r}
grady_augmented_dictionary <- 
  qdapDictionaries::GradyAugmented %>% 
  as_tibble()

colnames(grady_augmented_dictionary) <- "name"

mark_kantrowitzs_names_dictionary <- 
  read_tsv("http://www.cs.cmu.edu/afs/cs/project/ai-repository/ai/areas/nlp/corpora/names/other/names.txt", 
           col_names = "name") %>% 
  as_tibble()

dictionary <- 
  grady_augmented_dictionary %>% 
  bind_rows(mark_kantrowitzs_names_dictionary)
```

After excluding local governments that are inactive or dissolved, I searched for names that are blank, 
contain only numbers, or contain text like "Not Available", "Not Provided," "Unavailable", "NA," and "N/A." I found the following:
  
(NO "NOT APPLICABLE"s? Really?)
  
* Blank fields
* Fields containing some variation of "Not Provided"
* Fields containing some variation of "Not Available" (e.g., "N/A")
* Fields containing numbers unaccompanied by a name
* Fields containing incoherent or unhelpful names (e.g., a mixture of numbers and letters).

```{r, echo=FALSE}
exp_invalid_names <- 
  exp_names %>% 
  filter(vendor_name == "" |
           str_detect(vendor_name, regex("^not a", ignore_case = TRUE)) |
           str_detect(vendor_name, regex("^not pro", ignore_case = TRUE)) |
           str_detect(vendor_name, "^[0-9]+") |
           str_detect(vendor_name, regex("vendor id", ignore_case = TRUE)))

rev_invalid_names <- 
  rev_names %>% 
  filter(vendor_name == "" |
           str_detect(vendor_name, regex("^not a", ignore_case = TRUE)) |
           str_detect(vendor_name, regex("^not pro", ignore_case = TRUE)) |
           str_detect(vendor_name, "^[0-9]+"))

exp_number_of_entities_with_invalid_names <- 
  exp_invalid_names %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

rev_number_of_entities_with_invalid_names <- 
  rev_invalid_names %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

exp_number_of_entities_with_not_provided <- 
  exp_invalid_names %>% 
  filter(str_detect(vendor_name, regex("^not pro", ignore_case = TRUE))) %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

rev_number_of_entities_with_not_provided <- 
  rev_invalid_names %>% 
  filter(str_detect(vendor_name, regex("^not pro", ignore_case = TRUE))) %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

exp_number_of_entities_with_blank_or_number <- 
  exp_invalid_names %>% 
  filter(vendor_name == "" |
           str_detect(vendor_name, "^[0-9]+")) %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

rev_number_of_entities_with_blank_or_number <- 
  rev_invalid_names %>% 
  filter(vendor_name == "" |
           str_detect(vendor_name, "^[0-9]+")) %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

exp_number_of_distinct_invalid_names <- 
  exp_invalid_names %>% 
  distinct(vendor_name) %>% 
  count() %>% 
  as.numeric()

rev_number_of_distinct_invalid_names <- 
  rev_invalid_names %>% 
  distinct(vendor_name) %>% 
  count() %>% 
  as.numeric()
```

For expenses, there are:
  
  * `r exp_number_of_entities_with_invalid_names` vendor names that may be invalid.
* `r exp_number_of_distinct_invalid_names` unique vendor names.
* `r exp_number_of_entities_with_invalid_names` local governments with vendor names that may be invalid.
+ `r exp_number_of_entities_with_not_provided` local governments report at least one "Not Provided" vendor name.
+ `r exp_number_of_entities_with_blank_or_number` local governments report at least one blank name or a name including a number.

For revenues, there are:
  
  * `r rev_number_of_entities_with_invalid_names` vendor names that may be invalid.
* `r rev_number_of_distinct_invalid_names` unique vendor names.
* `r rev_number_of_entities_with_invalid_names` local governments with vendor names that may be invalid.
+ `r rev_number_of_entities_with_not_provided` local governments report at least one "Not Provided" vendor name.
+ `r rev_number_of_entities_with_blank_or_number` local governments report at least one blank name or a name including a number. 

```{r}
rm(exp_number_of_distinct_invalid_names,
   exp_number_of_entities_with_blank_or_number,
   exp_number_of_entities_with_invalid_names,
   exp_number_of_entities_with_not_provided,
   rev_number_of_distinct_invalid_names,
   rev_number_of_entities_with_blank_or_number,
   rev_number_of_entities_with_invalid_names,
   rev_number_of_entities_with_not_provided)
```

**Expense Invalid Name Totals, by Entity**
  
  ```{r}
exp_total_vendors <- 
  exp_names %>% 
  group_by(entity_name) %>% 
  summarise(total_vendors = n())

exp_entity_totals <- 
  exp_invalid_names %>% 
  group_by(entity_name) %>% 
  summarise(invalid_vendor_count = n()) %>% 
  left_join(exp_total_vendors, by = "entity_name") %>% 
  mutate(percent_invalid = (invalid_vendor_count / total_vendors) * 100) %>% 
  mutate(percent_invalid = round(percent_invalid, digits = 1)) %>% 
  select(entity_name, percent_invalid, invalid_vendor_count, total_vendors) %>% 
  arrange(desc(percent_invalid), desc(invalid_vendor_count)) %>% 
  print()
```

**Revenue Invalid Name Totals, by Entity**
  
  ```{r}
rev_total_vendors <- 
  rev_names %>% 
  group_by(entity_name) %>% 
  summarise(total_vendors = n())

rev_entity_totals <- 
  rev_invalid_names %>% 
  group_by(entity_name) %>% 
  summarise(invalid_vendor_count = n()) %>% 
  left_join(rev_total_vendors, by = "entity_name") %>% 
  mutate(percent_invalid = (invalid_vendor_count / total_vendors) * 100) %>% 
  mutate(percent_invalid = round(percent_invalid, digits = 1)) %>% 
  select(entity_name, percent_invalid, invalid_vendor_count, total_vendors) %>% 
  arrange(desc(percent_invalid), desc(invalid_vendor_count)) %>% 
  print()
```

**Expense Invalid Name Totals, by Entity, by Invalid Name** 
  
  ```{r, echo=FALSE}
exp_by_name_totals <- 
  exp_invalid_names %>% 
  group_by(entity_name, vendor_name) %>% 
  summarise(name_count = n()) %>% 
  left_join(exp_total_vendors, by = "entity_name") %>% 
  mutate(percent_invalid = (name_count / total_vendors) * 100) %>% 
  mutate(percent_invalid = round(percent_invalid, digits = 1)) %>% 
  select(entity_name, vendor_name, percent_invalid, name_count, total_vendors) %>%
  arrange(desc(percent_invalid, desc(name_count))) %>% 
  print()
```

**Revenue Invalid Name Totals, by Entity, by Invalid Name** 
  
  ```{r, echo=FALSE}
rev_by_name_totals <- 
  rev_invalid_names %>% 
  group_by(entity_name, vendor_name) %>% 
  summarise(name_count = n()) %>% 
  left_join(rev_total_vendors, by = "entity_name") %>% 
  mutate(percent_invalid = (name_count / total_vendors) * 100) %>% 
  mutate(percent_invalid = round(percent_invalid, digits = 1)) %>% 
  select(entity_name, vendor_name, percent_invalid, name_count, total_vendors) %>%
  arrange(desc(percent_invalid, desc(name_count))) %>% 
  print()
```

# DBMS Disconnection

```{r}
dbDisconnect()
```