---
title: "Identify Invalid Employee Names"
author: "Michael Jensen"
date: "September 2019"
output: html_notebook
---
# Program Description

**Purpose**

Identify entities that have reported invalid or potentially invalid employee names to Transparent Utah.

**Input(s)**

```{r}
dsn_aws        <- "transpAWS"
dsn_salesforce <- "Salesforce"
```

**Output(s)**



# Libraries and Data Sources

```{r}
library(odbc)
library(stringr)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_salesforce)
rm(dsn_aws, dsn_salesforce)
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}

```



# Execution

## Salesforce

Query active and particpating entities with employees:

```{r}
sf_data <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      Name               AS entity_name,
      Transparency_ID__c AS t_id
    FROM Account
    WHERE RecordTypeId IN (
      SELECT Id
      FROM RecordType
      WHERE DeveloperName IN (
        'AOG', 
        'City',
        'Conservation_District',
        'County', 
        'District_Health',     
        'Housing', 
        'Interlocal', 
        'Local_and_Special_Service_District', 
        'Mental_Health', 
        'Redevelopment_Agency_Project_Area', 
        'School_District_or_Charter_School',
        'Town'))
    AND Entity_Status__c IN (
      'Current',
      'On hold',
      'Delinquent',
      'Suspended')
    AND Id NOT IN (
      SELECT Transparency_Exemption__c.Account__c
      FROM Transparency_Exemption__c
      WHERE 
        Transparency_Exemption__c.Exemption_Reason__c LIKE 'Reports with%' 
      OR  
        Transparency_Exemption__c.Exemption_Reason__c LIKE 'No W-2%')")
```

##

```{r}

```

# DBMS Disconnection

```{r}
dbDisconnect()
```

# Code from old program

***
The purpose of this report is to identify local governments that may have reported invalid employee names to Transparency.

### Analysis

**Identify Invalid Names**

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message=FALSE}
# Packages & Data Connections
library(knitr)
library(odbc)
library(stringr)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
odbc_sf  <- dbConnect(odbc::odbc(), "Salesforce") 
```

```{sql, connection=odbc_sf, output.var="developer_name"}
SELECT DISTINCT DeveloperName
FROM RecordType
WHERE DeveloperName NOT IN (
 'Chat', 'Community', 'Email', 'Phone', 'Social', 'CPA_Firm', 'Community_User',
 'Educational_Foundation', 'Financial_Institution', 'State_Agency',
 'Justice_Court', 'Non_Profits', 'Subpoena', 'LT_Gov_Document', 'Consolidation', 
 'AUP_Checklist', 'Budget_Checklist', 'LEA_Checklist', 'Large_Entity_Checklist',
 'Small_Entity_Checklist', 'Special_Purpose_Audit')
```

```{sql, connection=odbc_sf, output.var="active_local_govs"}
SELECT Transparency_ID__c AS transparency_id,
       Name               AS sf_entity_name
FROM Account
WHERE RecordTypeId IN (
  SELECT Id
  FROM RecordType
  WHERE DeveloperName IN (
    'AOG', 
    'City',
    'Conservation_District',
    'County', 
    'District_Health',     
    'Housing', 
    'Interlocal', 
    'Local_and_Special_Service_District', 
    'Mental_Health', 
    'Redevelopment_Agency_Project_Area', 
    'School_District_or_Charter_School',
    'Town'))
AND Entity_Status__c IN (
  'Current',
  'On hold',
  'Delinquent',
  'Suspended')
```

```{sql, connection=odbc_sf, output.var="no_employees"}
SELECT Account.Name               AS sf_entity_name,
       Account.Transparency_ID__c AS transparency_id
FROM Account
WHERE Account.Id IN (
  SELECT Transparency_Exemption__c.Account__c
  FROM Transparency_Exemption__c
  WHERE Transparency_Exemption__c.Exemption_Reason__c LIKE 
    '%Reports with another entity%' OR
    Transparency_Exemption__c.Exemption_Reason__c LIKE '%No W-2 Employees%')
```

```{sql, connection=odbc_aws, output.var="govt_lvl"}
SELECT DISTINCT govt_lvl
FROM entity
```

Does the query below do what I want it to? I'm not certain I want the DISTINCT information.... do I?

```{sql, connection=odbc_aws, output.var="employee_names"}
SELECT DISTINCT vendor.id   AS employee_id,
                vendor.name AS employee_name,
                entity.id   AS transparency_id,
                entity.name AS entity_name
FROM vendor
LEFT JOIN entity
ON entity.id = vendor.entity_id
WHERE vendor.id IN(
  SELECT vendor_summary.vendor_id
  FROM vendor_summary
  WHERE type = 3)
AND vendor.entity_id IN (
  SELECT id
  FROM entity
  WHERE govt_lvl IN (
    'CITY',
    'COUNTY',
    'HOUSING AUTHORITIES',
    'INTERLOCAL',
    'INDEPENDENT',
    'K12 EDUCATION',
    'LOCAL DISTRICTS'
    'SERVICE DISTRICTS'))
```

```{r}
employee_names <- 
  employee_names %>% 
  as_tibble()

employee_names$employee_id <- 
  as.numeric(employee_names$employee_id)

employee_names$transparency_id <- 
  as.numeric(employee_names$transparency_id)

rm(developer_name, govt_lvl)
```

```{r}
employee_names <- 
  employee_names %>% 
  semi_join(active_local_govs, by = "transparency_id") %>% 
  anti_join(no_employees, by = "transparency_id")

distinct_names <- 
  employee_names %>% 
  distinct(employee_name) %>% 
  arrange(employee_name)

rm(active_local_govs, distinct_names, no_employees)
```

After excluding local governments that are inactive, dissolved, or that do not have employees, I searched the data for names that are blank, contain only numbers, or contain text like "Not Available", "Not Provided," "Unavailable", "NA," and "N/A." I found the following:

* Blank fields.
* Fields containing some variation of "Not Provided."
* Fields containing numbers unaccompanied by a name.

```{r}
invalid_names <- 
  employee_names %>% 
  filter(employee_name == "" |
         str_detect(employee_name, regex("^not ", ignore_case = TRUE)) |
         str_detect(employee_name, "^[0-9]+"))
  
number_of_entities <- 
  invalid_names %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

number_of_not_provided <- 
  invalid_names %>% 
  filter(str_detect(employee_name, regex("^not ", ignore_case = TRUE))) %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

number_of_blank_or_number <- 
  invalid_names %>% 
  filter(employee_name == "" |
         str_detect(employee_name, "^[0-9]+")) %>% 
  distinct(entity_name) %>% 
  count() %>% 
  as.numeric()

distinct_invalid_names <- 
  invalid_names %>% 
  distinct(employee_name)

number_of_distinct_invalid_names <- 
  distinct_invalid_names %>% 
  count() %>% 
  as.numeric()

rm(distinct_invalid_names)
```

By the numbers,

* There are `r number_of_distinct_invalid_names` invalid or potentially invalid names across `r number_of_entities` local governments (including variations of "Not Provided").
* There are `r number_of_blank_or_number` local governments that have reported a blank field or number as the employee name.
* There are `r number_of_not_provided` local governments that have reported a "Not Provided" name.

Per Transparency Board policy, the only valid entry for protected information is "Not Provided." Therefore,

* Blank fields and fields containing only numbers are invalid and local governments should correct that information.
* Local governments with a high percentage of "Not Provided" names should provide a reason for protecting so much information, or correct the names inappropriately identified as protected.

```{r}
rm(number_of_blank_or_number, number_of_distinct_invalid_names, 
   number_of_entities, number_of_not_provided)
```

**Invalid Employee Name Totals, by Entity**

```{r}
total_employees <- 
  employee_names %>% 
  group_by(entity_name) %>% 
  summarise(total_employees = n())

entity_totals <- 
  invalid_names %>% 
  group_by(entity_name) %>% 
  summarise(number_invalid = n()) %>% 
  left_join(total_employees, by = "entity_name") %>% 
  mutate(percent_invalid = (number_invalid / total_employees) * 100) %>% 
  mutate(percent_invalid = round(percent_invalid, digits = 1)) %>% 
  select(entity_name, percent_invalid, number_invalid, total_employees) %>% 
  arrange(desc(percent_invalid), desc(number_invalid)) %>% 
  kable(col.names = c("Entity Name", "% Invalid", "Number Invalid", 
                      "Total Employees"), 
        align = "l") %>% 
  print()
```

**Invalid Employee Names, by Entity, by Invalid Name**

```{r}
name_totals <- 
  invalid_names %>% 
  group_by(entity_name, employee_name) %>% 
  summarise(number_of_entries = n()) %>% 
  left_join(total_employees, by = "entity_name") %>% 
  mutate(percent_invalid = (number_of_entries / total_employees) * 100) %>% 
  mutate(percent_invalid = round(percent_invalid, digits = 1)) %>% 
  select(entity_name, employee_name, percent_invalid, number_of_entries,
         total_employees) %>% 
  arrange(desc(percent_invalid), desc(number_of_entries)) %>% 
  kable(col.names = c("Entity Name", "Employee Name", "% Invalid", 
                      "Number Invalid", "Total Employees"), 
        align = "l") %>% 
  print()
```

```{r}
dbDisconnect(odbc_aws)
dbDisconnect(odbc_sf)
rm(list = ls())
```