---
title: "Mail Merge v 2.0"
author: "Michael Jensen"
date: "August 2019"
output: html_notebook
---
# Program Description

**Purpose**

Compile and format the information needed to send the 60-day Warning postcards or the Hold/Suspend Notices to local governments that are non-compliant with OSA or State Treasurer reporting requirements.

*This R program is based on Alexandra Nelson's "MailMerge Script, which is filed in S:\Localgov\LG Compliance\Compliance\Noncompliance Correspondence"*

**Input(s)**

```{r}
dsn_sf <- "Salesforce"

# Select the appropriate notice type:
notice_type <- 
  # "60_day_notice"
  "hold_or_suspend"
```

**Output(s)**

A .csv file containing a record for each entity that is missing a required Transparent Utah report, with the following fields:

* Entity name
* Entity CFO name
* Entity CAO name
* Entity address information
* A field for each report the entity is missing

A .csv file containing a record for each entity that is missing a required OSA or State Treasurer report, with the following fields:

* Entity name
* Entity CFO name
* Entity CAO name
* Entity address information
* A field for each report the entity is missing

**Comments**

The Missing D & I Report comes from the Office of the State Treasurer. Though they have an instance of Salesforce, they don't actively use it (as of 2019-09-20). I can't, therefore, pull the missing reports from Salesforce and integrate them in the report I create here. Right now, our workflow consists of someone from the Treasurer's Office emailing us a list of entities that are missing reports, which we then manually enter into this report.

# Libraries and Data Sources

```{r}
library(data.table)
library(janitor)
library(magrittr)
library(odbc)
library(readxl)
library(splitstackshape)
library(svDialogs)
library(tidyverse)

odbc_salesforce <- dbConnect(odbc::odbc(), dsn_sf)

rm(dsn_sf)
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}
  # Arguments:
  #  address_one (char): The portion of the complete address corresponding to 
  #    street_one.
  #  address_two (char): The portion of the complete address corresponding to 
  #    street_two.
  #  street_one (char): The default street address.
  #  street_two (char): The street address to compare against.
```

## find_an_address()

```{r}
find_an_address <- function(street_one, street_two, address_one, address_two) {
  # Compare two street addresses and select the corresponding address 
  # information for the street address that is not NA.
  #
  # Arguments:
  #  street_one (char): The default street address.
  #  street_two (char): The street address to compare against.
  #  address_one (char): The portion of the complete address corresponding to 
  #    street_one.
  #  address_two (char): The portion of the complete address corresponding to 
  #    street_two.
  #
  # Returns:
  #   Character.
  
  if (is.na(street_one) && !is.na(street_two)) {
    
    address_two
  
  } else {address_one}
}
```

# Execution

## Salesforce - Contact Information

```{r}
account <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT 
      a.Id                         AS sf_id,
      a.Name                       AS entity_name, 
      r.Name                       AS record_type,
      a.Is_Solely_Fee_Assessing__c AS non_taxing_entity,
      a.ShippingStreet, a.ShippingCity, a.ShippingState, a.ShippingPostalCode,
      a.BillingStreet, a.BillingCity, a.BillingState, a.BillingPostalCode,
      a.Mailing_county__c          AS mailing_county,
      a2.Name                      AS tax_holding_county,
      a.FINET_Vendor_Code__c       AS finet_code
    FROM Account AS a
    LEFT JOIN RecordType AS r
    ON a.RecordTypeId = r.Id
    LEFT JOIN Account AS a2
    ON a.Tax_Holding_County__c = a2.Id
    WHERE a.IsDeleted = FALSE
    AND a.Entity_Status__c NOT IN ('Inactive', 'Dissolved')
    AND a.Name <> 'test city 2'
    AND a.RecordTypeId IN (
      SELECT id
      FROM RecordType
      WHERE Name IN (
        'AOG', 'City', 'Community Reinvestment Agency', 'Conservation District',
        'County', 'District Health', 'Housing', 
        'Independent/Quasi State Entity', 'Interlocal', 
        'Local and Special Service District', 'Mental Health', 'Non Profits',
        'Redevelopment Agency/Project Area', 
        'School District or Charter School', 'Town'))") %>% 
  mutate(street = pmap_chr(
                    list(
                      street_one  = as.list(ShippingStreet),
                      street_two  = as.list(BillingStreet),
                      address_one = as.list(ShippingStreet),
                      address_two = as.list(BillingStreet)),
                    find_an_address),
         city   = pmap_chr(
                    list(
                      street_one  = as.list(ShippingStreet),
                      street_two  = as.list(BillingStreet),
                      address_one = as.list(ShippingCity),
                      address_two = as.list(BillingCity)),
                    find_an_address),    
         state   = pmap_chr(
                    list(
                      street_one  = as.list(ShippingStreet),
                      street_two  = as.list(BillingStreet),
                      address_one = as.list(ShippingState),
                      address_two = as.list(BillingState)),
                    find_an_address),         
         zip     = pmap_chr(
                    list(
                      street_one  = as.list(ShippingStreet),
                      street_two  = as.list(BillingStreet),
                      address_one = as.list(ShippingPostalCode),
                      address_two = as.list(BillingPostalCode)),
                    find_an_address)) %>% 
  select(sf_id, entity_name, record_type, non_taxing_entity, 
         street, city, state, zip, mailing_county, tax_holding_county,
         finet_code)

# CFOs and CAOs sometimes have an address that is different from the entity's
# address. Though it would be more convenient for the CFO and CAO to receive the 
# notice at the address specific to their contact information, I decided to 
# send notices to the entity address. Given that the CFO and CAO can change 
# without notifying OSA, it seems that sending the notice to the entity's 
# address is the best way to make sure that someone within the entity 
# organization will see it.

cfo <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT
      a.Name            AS entity_name, 
      c.Name            AS cfo_name
      -- MailingStreet     AS cfo_street, 
      -- MailingCity       AS cfo_city, 
      -- MailingState      AS cfo_state, 
      -- MailingPostalCode AS cfo_zipcode
    FROM Contact AS c
    JOIN Account AS a
    ON c.AccountId = a.Id
    WHERE c.IsDeleted = FALSE
    AND c.IsDeactivated__c = FALSE
    AND Role__c = 'CFO'")

cao <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT
      a.Name            AS entity_name, 
      c.Name            AS cao_name
      -- MailingStreet     AS cao_street, 
      -- MailingCity       AS cao_city, 
      -- MailingState      AS cao_state, 
      -- MailingPostalCode AS cao_zipcode
    FROM Contact AS c
    JOIN Account AS a
    ON c.AccountId = a.Id
    WHERE c.IsDeleted = FALSE
    AND c.IsDeactivated__c = FALSE
    AND Role__c = 'CAO'")

# Check for entities with multiple CFOs:
multiple_cfos <- 
  cfo[duplicated(cfo$entity_name), "entity_name"] %>% 
  tibble(has_multiple_cfos = .) %>% 
  distinct(has_multiple_cfos) %>% 
  arrange(has_multiple_cfos)

multiple_caos <- 
  cao[duplicated(cao$entity_name), "entity_name"] %>% 
  tibble(has_multiple_caos = .) %>% 
  distinct(has_multiple_caos) %>% 
  arrange(has_multiple_caos)

if (nrow(multiple_cfos) > 0 || nrow(multiple_caos) > 0) {
  
  dlg_message(
    "Salesforce has at least one entity with multiple CFOs or CAOs.
    See report of entities with multiple cfos or caos.
    This program will select one of the names to send a notice to.")
  
  file_path <-
    "S:/Localgov/Database/Salesforce/Reports/"
  
  multiple_cfos %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), " Entities with Multiple CFOs.csv"),
      na = "")
  
  multiple_caos %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), " Entities with Multiple CAOs.csv"),
      na = "")
  
  cfo <- 
    cfo %>% 
    data.table() %>% 
    unique(by = "entity_name")

  cao <- 
    cao %>% 
    data.table() %>% 
    unique(by = "entity_name")
}

contact_info <- 
  account %>% 
  left_join(cfo, by = "entity_name") %>% 
  left_join(cao, by = "entity_name") %>% 
  mutate(cfo_name = if_else(is.na(cfo_name), "CFO", cfo_name),
         cao_name = if_else(is.na(cao_name), "CAO", cao_name)) %>% 
  select(entity_name, non_taxing_entity, cfo_name, cao_name, street, city, 
         state, zip, record_type, sf_id, mailing_county, tax_holding_county,
         finet_code) %>% 
  arrange(entity_name)

rm(cao, cfo, account)

if (exists("file_path")) rm(file_path)
```

## Salesforce - Missing OSA Reports

Notes:

* We send 10-day notices for missing budgets, and those are handled by the Office Specialist (currently, Brooke), so I don't query those reports here.
* Originally, the query below to the `Reports__c` Table included `AND Required__c = TRUE`. Brooke told me that there are instances when a report should be required, but neither Salesforce nor the person reviewing the report notices the "Required" checkbox isn't selected. So, I decided to list the report types that we care about. This means that this list may need to be reviewed and compared to the list in Salesforce, to verify that any new report types are captured here.

```{r}
report_year <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT 
      Name AS report_year, 
      Id
    FROM Report_Year__c
    WHERE IsDeleted = FALSE
    AND Delinquent_Reports__c > 0")

reports__c <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT
      a.Name AS entity_name, 
      Report_Type__c AS missing_report,
      Report_Status__c
    FROM Reports__c AS r
    LEFT JOIN Account AS a
    ON r.Account__c = a.Id
    WHERE r.IsDeleted = FALSE
    AND Delinquent__c = TRUE
    AND r.Report_Type__c IN (
      'Agreed-Upon Procedures',
      'Agreed Upon Procedures',
      'AUP',
      'Financial Certification',
      'Financial Report',
      'Impact Fee',
      'Impact Fee Report',
      'Impact Fees',
      'Self-Evaluation Form',
      'Self Evaluation Form')
    AND r.Entity_Type__c IN (
      SELECT Name
      FROM RecordType
      WHERE Name IN (
        'AOG', 'City', 'Community Reinvestment Agency', 'Conservation District',
        'County', 'District Health', 'Housing', 'Independent/Quasi State Entity',
        'Institution of Higher Education', 'Interlocal', 
        'Local and Special Service District', 'Mental Health', 'Non Profits', 
        'Redevelopment Agency/Project Area', 'School District or Charter School',
        'Town'))
    AND a.Entity_Status__c IN (
      'Current',
      'Delinquent',
      'Suspended',
      'On hold')")

missing_reports_osa <- 
  reports__c %>% 
  left_join(report_year, by = c("Report_Status__c" = "Id")) %>% 
  unite(missing_report, report_year, missing_report, sep = " ") %>% 
  select(-Report_Status__c)

missing_reports_osa <- 
  missing_reports_osa %>% 
  group_by(missing_report) %>% 
  # See how many reports of each type are missing with summarize():
  summarize(n = n()) %>% 
  rowid_to_column("report_id") %>% 
  select(-n) %>% 
  right_join(missing_reports_osa, by = "missing_report")

missing_reports_osa <- 
  missing_reports_osa %>% 
  spread(report_id, missing_report)

# Alex had the group_by(), summarize_all(), and mutate_all() functions piped as 
# the last two lines in the code above. I'm not sure why, as it looks like she 
# removed the NA values just to add them back in again with the next line of 
# code. I'll keep it for now, in case I discover why she did this.
  #  %>% 
  # group_by(entity_name) 
  # summarize_all(funs(toString(na.omit(.)))) %>% 
  # mutate_all(funs(replace(., . == 0, NA)))

missing_reports_osa[missing_reports_osa == ""] <-  NA

# Shift reports to the left:
missing_reports_osa2 <- 
  as.data.frame(
    t(
      apply(
        missing_reports_osa, 
        1, 
        function(x){return(c(x[!is.na(x)], x[is.na(x)]))})))

colnames(missing_reports_osa2) <- colnames(missing_reports_osa)

missing_reports_osa <- missing_reports_osa2

rm(report_year, reports__c, missing_reports_osa2)

for (j in 2:length(missing_reports_osa)) {
  
  colnames(missing_reports_osa)[j] <- paste("Auditor ", j - 1)
  
}
rm(j)

missing_reports_osa <- 
  missing_reports_osa %>% 
  remove_empty("cols")

missing_reports_osa$entity_name <- 
  as.character(missing_reports_osa$entity_name)
```

## Missing Transparency Reports

Comments:

* In the code below, I filter the data using `max(created_date)`. Doing so works in this program, because the trigger for running this program is an initial or post-60-day grace period Compliance Report uploaded to Salesforce. Thus, every active and participating entity in the Salesforce database will have the same value for `created_date`. 

Were, for whatever reason, any one entity to have a Compliance Report entry with a more recent `created_date` value than the others, the code below would return only that entity. I don't expect we would run this Mail Merge code without doing a Compliance Report for every entity, so I won't spend time addressing a problem that I don't expect to occur.

* The code below relies on Salesforce correctly assigning a Transparency status to each entity's most recent Compliance Report entry (as made apparent on 2019-10-04, the 60th day of the compliance cycle and the date we ran this Mail Merge program to generate the Hold/Suspend Notice postcards). If Salesforce incorrectly assigns the Transparency status, then the first query below will select records with a status of `Delinquent_Enforced` or `Hold` from a previous Compliance Report entry. Though I'm expecting this problem will be solved soon, I've written a second query (commented out) that will allow us to work around the problem in Salesforce (it's not a perfect solution, but is good enough).

```{r}
missing_reports_transp <- 
  dbGetQuery(
    odbc_salesforce,
    "SELECT 
      a.Name AS entity_name,
      t.Expenditure_Problem__c AS missing_exp,
      t.Revenue_Problem__c AS missing_rev,
      t.Wage_Problem__c AS missing_w2,
      t.CreatedDate AS created_date
    FROM Transparency_Reporting__c AS t
    JOIN Account AS a
    ON t.Account__c = a.Id
    WHERE t.IsDeleted = FALSE
    AND Status__c IN ('Delinquent_Enforced', 'Hold')
    AND Account__c IN (
      SELECT Id
      FROM Account
      WHERE RecordTypeId IN (
        SELECT Id
        FROM RecordType
        WHERE Name IN (
          'AOG', 'City', 'Community Reinvestment Agency', 
          'Conservation District', 'County', 'District Health', 'Housing',
          'Independent/Quasi State Entity', 'Institution of Higher Education',
          'Interlocal', 'Local and Special Service District', 'Mental Health',
          'Non Profits', 'Redevelopment Agency/Project Area', 
          'School District or Charter School', 'Town')))") %>% 
  mutate(created_date = as.Date(created_date)) %>% 
  filter(created_date == max(created_date)) %>% 
  # select(-created_date) %>% 
  cSplit(
    c("missing_exp", "missing_rev", "missing_w2"),
    sep = ", ",
    direction = "wide") %>%
  remove_empty("cols")

# Use the query below when Salesforce incorrectly assigns the Transparency 
# status:
#
# missing_reports_transp <-
#   dbGetQuery(
#     odbc_salesforce,
#     "SELECT
#       a.Name AS entity_name,
#       t.Expenditure_Problem__c AS missing_exp,
#       t.Revenue_Problem__c AS missing_rev,
#       t.Wage_Problem__c AS missing_w2,
#       t.CreatedDate AS created_date
#     FROM Transparency_Reporting__c AS t
#     JOIN Account AS a
#     ON t.Account__c = a.Id
#     WHERE t.IsDeleted = FALSE
#     AND Temporary_Exemption__c <> 1
#     AND Still_Missing_Noticed_Periods__c = 1
#     AND Account__c IN (
#       SELECT Id
#       FROM Account
#       WHERE RecordTypeId IN (
#         SELECT Id
#         FROM RecordType
#         WHERE Name IN (
#           'AOG', 'City', 'Community Reinvestment Agency',
#           'Conservation District', 'County', 'District Health', 'Housing',
#           'Independent/Quasi State Entity', 'Institution of Higher Education',
#           'Interlocal', 'Local and Special Service District', 'Mental Health',
#           'Non Profits', 'Redevelopment Agency/Project Area',
#           'School District or Charter School', 'Town')))") %>%
#   mutate(created_date = as.Date(created_date)) %>%
#   filter(created_date == max(created_date)) %>%
#   select(-created_date) %>%
#   cSplit(
#     c("missing_exp", "missing_rev", "missing_w2"),
#     sep = ", ",
#     direction = "wide") %>%
#   remove_empty("cols")
```

## Merge Reports with Contact Information

```{r}
report_send_notices_osa <- 
  contact_info %>% 
  right_join(missing_reports_osa, by = "entity_name")

report_send_notices_transp <- 
  contact_info %>% 
  right_join(missing_reports_transp, by = "entity_name")

# While revising this program, I discovered a few duplicate entities. I think 
# my revisions corrected the problem, but I'll keep the code below for now.
duplicate_osa <- duplicated(report_send_notices_osa$entity_name)

duplicate_transp <- duplicated(report_send_notices_transp$entity_name)

report_send_notices_osa <- 
  report_send_notices_osa[!duplicate_osa, ]

report_send_notices_transp <- 
  report_send_notices_transp[!duplicate_transp, ]

rm(missing_reports_osa, missing_reports_transp, missing_reports, 
   contact_info, duplicate)

# Export reports:

file_path <-
  "S:/Localgov/LG Compliance/Transparency Compliance/Compliance Reports/"

if (notice_type == "60_day_notice") {
  
  report_send_notices_osa %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), 
                    " Mail Merge 60-day Notice OSA.csv"),
      na = "")
  
  report_send_notices_transp %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), 
                    " Mail Merge 60-day Notice Transp.csv"),
      na = "")
  
} else if (notice_type == "hold_or_suspend") {
  
  report_send_notices_osa %>% 
    filter(is.na(non_taxing_entity) | non_taxing_entity == FALSE) %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), 
                    " Mail Merge Hold Notice OSA.csv"),
      na = "")
  
  report_send_notices_transp %>% 
    filter(is.na(non_taxing_entity) | non_taxing_entity == FALSE) %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), 
                    " Mail Merge Hold Notice Transp.csv"),
      na = "")
  
  report_send_notices_osa %>% 
    filter(non_taxing_entity == TRUE) %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), 
                    " Mail Merge Suspend Notice OSA.csv"),
      na = "")
  
  report_send_notices_transp %>% 
    filter(non_taxing_entity == TRUE) %>% 
    write_csv(
      path = paste0(file_path, Sys.Date(), 
                    " Mail Merge Suspend Notice Transp.csv"),
      na = "")
}
```

# DBMS Disconnection

```{r}
dbDisconnect()
```