---
title: "Review Transparent Utah IDs"
author: "Michael Jensen"
output: html_notebook
---
# Program Description

**Purpose**

Compare the Transparent Utah IDs in Salesforce to those in the Transparent Utah database, for active, inactive, and dissolved entities, in order to identify discrepancies.

**Input(s)**

* The name of the ODBC connection to AWS.
* The name of the ODBC connection to Salesforce.

```{r}
dsn_aws <- "transpAWS"
dsn_sf  <- "Salesforce"
```

**Output(s)**

* Report: IDs Unique to Salesforce
  * For active entities that do not report with a parent entity.
* Report: IDs Unique to Transparent Utah
* Report: IDs Shared by Salesforce and Transparent Utah

# Libraries and Data Sources

```{r, message=FALSE}
library(odbc)
library(stringdist)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_sf)
rm(dsn_aws, dsn_sf)
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}
  #
```


# Execution

## Import Entity Names and Transparent Utah IDs

```{r}
ids_aws <- 
  dbGetQuery(
    odbc_aws,
    "SELECT id AS t_id, name AS entity_name FROM entity") %>% 
  mutate(t_id = t_id %>% as.numeric()) %>%
  # Filter out entity names that are duplicates or nonsensical:
  filter(!entity_name %in% c(
    "",
    "AVAILABLE",
    "Canyon Land County Improvement District(Replaced)",
    "Grand County Water Conservancy District (Duplicate",
    # Replaced by Weber Morgan Strike Force w/t_id 1437:
    "Weber Morgan Narcotics Strike Force (Weber County)",
    "Wellsville-Mendon Conservation District (DUPLICATE",
    "x",
    "xk12",
    "xxk12",
    "XXSSD",
    "z Available for Use 1",
    "z Available for Use 2",
    "zz",
    "zzzz",
    "zzzzz")) %>% 
  as_tibble()

ids_sf <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      a.Transparency_ID__c AS t_id,
      a.Name AS entity_name,
      a.Entity_Status__c AS entity_status,
      r.Name AS govt_type
    FROM Account AS a
    LEFT JOIN RecordType AS r
      ON a.RecordTypeID = r.id
    WHERE a.RecordTypeId IN (
      SELECT Id
      FROM RecordType
      WHERE SobjectType = 'Account'
      AND IsActive = 'TRUE'
      AND Name NOT IN (
        'Community User',
        'Component', -- This govt type contains local governments, but not ones
                     -- for which we enforce compliance.
        'Court (Search Under Parent Entity)',
        'CPA Firm',
        'Educational Foundation or Component Unit', -- Not an entity we review
                                                    -- for compliance.
        'Financial Institution',
        'Health Provider',
        'Non Profits'))
    AND a.Name <> 'test city 2'") %>% 
  as_tibble() %>% 
  mutate(
    govt_type = 
      if_else(
        entity_name %in% 
          c("State of Utah",
            "Utah System of Higher Education - Student Loan Guarantee Program",
            "Utah System of Higher Education - Student Loan Purchase Program",
            "Utah System of Higher Education - Utah Educational Savings Plan dba my529",
            "Utah System of Higher Education - Utah State Board of Regents"),
        "Monitored State Agency",
        govt_type)) %>% 
  filter(govt_type != "State of Utah (agencies/depts/comp units/ etc.)")
```

## Report: IDs Unique to Salesforce

For active entities that do not report with a parent entity.

```{r}
entities_reporting_with_parent <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      a.Name AS entity_name
    FROM Account AS a
    LEFT JOIN Transparency_Exemption__c AS t
      ON a.Id = t.Account__c
    WHERE Transparency_ID__c IS NULL
    AND Exemption_Reason__c LIKE '%Reports with another entity%'
    AND (
      Exemption_End_Date__c IS NULL OR
      Exemption_End_Date__c >= DATE())")

report_ids_unique_sf <- 
  ids_sf %>% 
  anti_join(ids_aws, by = "t_id") %>% 
  filter(!entity_status %in% c("Inactive", "Dissolved")) %>% 
  anti_join(entities_reporting_with_parent, by = "entity_name") %>% 
  select(-t_id) %>% 
  arrange(govt_type)

rm(entities_reporting_with_parent)
```

## Report: IDs Unique to Transparent Utah

```{r}
report_ids_unique_aws <- 
  ids_aws %>% 
  anti_join(ids_sf, by = "t_id")
```

## Report: IDs Shared by Salesforce and Transparent Utah

```{r}
report_ids_shared$entity_name_aws %>% 
  str_to_lower() %>% 
  str_remove("//.") %>%
  str_remove("#") %>% 
  str_remove("center") %>% 
  str_remove("charter") %>% 
  str_remove("city") %>% 
  str_remove("cnty") %>%
  str_remove("county") %>% 
  str_remove("corporation") %>% 
  str_remove("corp") %>% 
  str_remove("dissolved") %>% 
  str_remove("school") %>% 
  str_remove("schools") %>% 
  str_remove("ssd") %>% 
  str_remove("special service district") %>% 
  str_remove("town") %>% 
  str_to_title()

remove_nonessential_words <- function() {
  
  
}
```

```{r}
report_ids_shared <- 
  ids_aws %>% 
  left_join(ids_sf, by = "t_id", suffix = c("_aws", "_sf"))%>% 
  mutate(
    entity_name_aws = 
      str_to_title(entity_name_aws) %>% 
      str_remove(" City") %>% 
      str_remove(" County") %>% 
      str_remove("Corporation"),
    entity_name_sf  = 
      str_to_title(entity_name_sf) %>% 
      str_remove(" City") %>% 
      str_remove(" County"),
    string_dist = 
      stringdist(entity_name_aws, entity_name_sf, method = "jw")) %>% 
  arrange(desc(string_dist))
```

## Export

```{r}
# Export the shared IDs and use Excel's Fuzzy Match add-in to compare columns:
report_ids_shared %>% 
  write_csv(
    file = "~/Shared Transparency IDs.csv")

report_ids_unique_aws %>% 
  write_csv(
    file = "~/Unique AWS Entities.csv")

report_ids_unique_sf %>% 
  write_csv(
    file = "~/Unique SF Entities.csv")
```

# DBMS Disconnection

```{r}
dbDisconnect(odbc_aws, odbc_sf)
```